---
title: "New LCM"
author: "Marina Chaji"
date: "8/16/2021"
output: html_document
---
# Load Packages
## First time use 

```{r setup, include=FALSE}

install.packages("leaflet")
install.packages("tidyverse")
install.packages("sf")
install.packages("ggplot2")
install.packages("RODM")
install.packages("ROracle")
install.packages("dplyr")
install.packages("dbplyr")
install.packages("tidyverse")
install.packages("raster")
install.packages("rgdal")


```

## After first time use

```{Library call}

library("leaflet")
library("tidyverse")
library("sf")
library("ggplot2")
library("RODM")
library("ROracle")
library("dbplyr")
library("dplyr")
library("RODBC")
library("raster")
library("rgdal")


```

# Load Offshore Wind Tool Data sets 

```{r Data Set Loading, echo=FALSE}

load("~/offshoreWind-master/data/APSD_DMIS_2.rda")
load("~/offshoreWind-master/data-raw/REVENUEFILE.Rdata")

```

# Loading Data fom Oracle 
## VTR Data
```{r, echo=FALSE}
#### Oracle login credentials
oracle_username = "mchaji"
oracle_password = "1234"
oracle_server = "sole"
ODBC.CONNECTION <- RODBC::odbcConnect(dsn=oracle_server, uid=oracle_username, pwd=oracle_password, believeNRows=FALSE)
START.YEAR = 2007
END.YEAR = 2019
for(i in START.YEAR:END.YEAR) {
  print(i)
  CURRENT.QUERY = paste("SELECT VTR.veslog",i,"t.TRIPID,tripcatg, operator, opernum, permit, nsubtrip, crew,not_fished  
                FROM VTR.veslog",i,"t", sep="")
  YEAR.RESULT = sqlQuery(ODBC.CONNECTION, CURRENT.QUERY)  
  
  # Now, the loop compiles the results; the first year must be treated slightly differently###
  if (i==START.YEAR) {
    RESULT.COMPILED = YEAR.RESULT
  } else {
    RESULT.COMPILED = rbind(RESULT.COMPILED, YEAR.RESULT) }
}    # End Main Loop


##Subtrip Data

ODBC.CONNECTION <- RODBC::odbcConnect(dsn=oracle_server, uid=oracle_username, pwd=oracle_password, believeNRows=FALSE)
  CURRENT.QUERY = paste ("SELECT VTR.veslog",i,"t.TRIPID,tripcatg, operator, opernum, permit, nsubtrip, crew,not_fished  
                FROM VTR.veslog",i,"t", sep="")
  VTR.veslog2019t = sqlQuery(ODBC.CONNECTION, CURRENT.QUERY) 



```

# Loading Data fom Oracle 
## Permit Data
```{r Data Set Loading, echo=FALSE}

ODBC.CONNECTION <- RODBC::odbcConnect(dsn=oracle_server, uid=oracle_username, pwd=oracle_password, believeNRows=FALSE)
  CURRENT.QUERY = paste ("SELECT vp_num, ap_num, plan
                         FROM vps_gear")
  vps_gear = sqlQuery(ODBC.CONNECTION, CURRENT.QUERY)  
  
  
ODBC.CONNECTION <- RODBC::odbcConnect(dsn=oracle_server, uid=oracle_username, pwd=oracle_password, believeNRows=FALSE)
  CURRENT.QUERY = paste ("SELECT ap_year, ap_num, name_first, name_middle, name_last, name_suffix, corp_name
                         FROM vps_owner")
  vps_owner = sqlQuery(ODBC.CONNECTION, CURRENT.QUERY)
  # End Main Loop
odbcCloseAll()
```



# Cleaning 
## 1. Filter down to only Scallop Species 
## 2. Seperate Dates & Times and Delete Old Dates Column 
## 3. Delete Columns that are not need 
### NESPP3 & SOURCE Values are all the same so this is deleted 


```{r, echo=FALSE}

Scallops <- APSD_DMIS_2 %>% filter (SPPNAME == "SCALLOPS/BUSHEL")

#Separate Dates & Times
Scallops$Date <- as.Date(Scallops$DATE_TRIP)
Scallops$Time <- format(Scallops$DATE_TRIP,"%H:%M:%S")

#Drop columns that are not needed
Scallops$DATE_TRIP<- NULL
Scallops$NESPP3<- NULL
Scallops$SOURCE<- NULL

```




# Merging
## 1. Merge Scallops & VTR.veslog2019t Data Sets
### This will be done in a way that keeps all columns 

## 2. Join Permit data (vps_owner & vps_gear) by application number
```{r, echo=FALSE}

## 1. 
#Join pulled data to DMIS data by TRIPIDs
# all.x = TRUE & all.y = FALSE means I am keeping data with no match from DMIS table but dropping data with no match from the Veslog tables
# DOCID is used because of the following found in the data dictionary "VESLOG Trip record identifier, which is generated internally; Primary key for VESLOGyyyyT; Foreign key to VESLOGyyS, VESLOGyyG. Equivalent to DOCID in VTR DOCUMENT table"
veslogDMISmerge <- merge(VTR.veslog2019t,Scallops, by.x = "TRIPID", by.y = "DOCID", all.x = FALSE, all.y = TRUE)
##


## 2. 
###Join Permit data (vps_owner & vps_gear) by application number
  # all = TRUE means a complete merge is done of the same variable (in this case being vp_num)
  permitmerge <- merge(vps_gear, vps_owner, all= TRUE)
 
  
```



# Data Cleaning
## veslogDMISmerge == Veslog & VTR Combined cleaning
###  1. Take out subtrips that are more than 2
###  2. Aggregate DOLLAR, POUNDS, LANDED
#### 3. Add back into veslogDMISmerge (L3)
```{r, echo=FALSE}

#### This filters out all nsubtrips above 2 while keeping NA values
veslogDMISmerge_L3_Subtrip <- veslogDMISmerge %>% filter(is.na(NSUBTRIP) | NSUBTRIP < 3)
#Tests to make sure filter works then delete set after
veslogDMISmerge_L3_Subtrip_Upper_Check <- veslogDMISmerge %>% filter(NSUBTRIP > 3)
veslogDMISmerge_L3_Subtrip_Upper_Check <- NULL


### Aggregate 
PostSub_Agg <- veslogDMISmerge_L3_Subtrip %>%
  group_by(TRIPID) %>%
 summarise(Agg_DOLLAR = sum(DOLLAR), Agg_POUNDS = sum(POUNDS), Agg_LANDED = sum(LANDED))

## Re-Combine with veslogDMISmerge_L3_Subtrip Data Set
PostSub_Agg_Veslog_Combo <- merge(veslogDMISmerge_L3_Subtrip,PostSub_Agg, by.x = "TRIPID", by.y = "TRIPID", all= FALSE)
```




# Data Cleaning
## 1. Check / Test Maximum DOLLAR values by grouping by TRIPID
## 2. Drop duplicate TRIPIDs by keeping maximum DOLLAR values 
## 3. Take out values on Land

```{r, echo=FALSE}

## Parse out Maximum Dollar amounts in order to drop lesser subtrips
MaxAttempt <- PostSub_Agg_Veslog_Combo %>% group_by(TRIPID) %>% filter(DOLLAR == max (DOLLAR))


### Remove duplicates by only keeping TRIPID with the highest DOLLAR value 
Duplicate_Post_V_Combo <- distinct(MaxAttempt, TRIPID, .keep_all = TRUE)
### Check to make sure all duplicate values are gone 
Check <- Duplicate_Post_V_Combo %>% group_by(TRIPID) %>% filter(n()>1)

### Remove land points by combining with water raster findings


```



## Fixing Looping pull eror for VTR Data 
```{r, echo=FALSE}



#Oracle Credentials and Data Pull Example
#percent-y only selects previous year but if you remove it pulls all years 
yr <- as.integer(format(Sys.time(),"%Y")) - 1
for(year in 2007:2019) {
  
  get_data <- function(){
    
    db <-config::get("database")
    drv <- dbDriver("Oracle")
    
    connect.string<-paste(
      "(DESCRIPTION=",
      "(ADDRESS=(PROTOCOL=tcp)(HOST=", db$host, ")(PORT=", db$port, "))",
      "(CONNECT_DATA=(SID=", db$sid, ")))", sep="")
    
    con <- dbConnect(drv, db$uid, db$pwd, dbname=connect.string)
    
    query = sprintf("SELECT tripid, tripcatg, operator, opernum, permit, nsubtrip, crew, not_fished
FROM VTR.veslog2019t WHERE tripcatg = 1 AND not_fished = 0")
    rs <- dbSendQuery(con,query)
    vtrt2019 <<- fetch(rs, n=-1)
    dbClearResult(rs)
    
    
    
    dbDisconnect(con)
  }
}

get_data()


#




Water_Only_Post_DPVC <- full_join (Duplicate_Post_V_Combo, vtrt2019, by = "TRIPID")
 

Water_Only_Post_DPVC <- Water_Only_Post_DPVC %>% rename(OPERNUM = OPERNUM.x, OPERATOR = OPERATOR.x, PERMIT = PERMIT.x.x, NSUBTRIP = NSUBTRIP.x, CREW = CREW.x,IMGID = IMGID.x, YEAR = YEAR.x, VTR_PORT = VTR_PORT.x , VTR_STATE = VTR_STATE.x, TRIP_LENGTH = TRIP_LENGTH.x)

Water_Only_Post_DPVC <- Water_Only_Post_DPVC %>% rename(DOLLAR = DOLLAR.x, POUNDS = POUNDS.x, LANDED = LANDED.x, DDLON = DDLON.x, DDLAT = DDLAT.x, GEARCODE = GEARCODE.x, SECGEARFISH = SECGEARFISH.x, SPPNAME = SPPNAME.x, Date = Date.x, Time = Time.x, Agg_DOLLAR = Agg_DOLLAR.x, Agg_POUNDS = Agg_POUNDS.x, Agg_LANDED = Agg_LANDED.x)

Water_Only_Post_DPVC = subset(Water_Only_Post_DPVC,select = -c(IMGID.y, PERMIT.y.y, DEALNUM.y,DOLLAR.y,POUNDS.y,LANDED.y, GEARCODE.y, SECGEARFISH.y, Date.y, Time.y, Agg_DOLLAR.y))

Water_yr_merge <- Water_Only_Post_DPVC %>% left_join(vtrt2019, by = "TRIPID")

Water_yr_merge <- Water_yr_merge %>% mutate(PERMIT = coalesce(PERMIT.x,PERMIT.y), OPERATOR = coalesce(OPERATOR.x, OPERATOR.y), NSUBTRIP = coalesce(NSUBTRIP.x,NSUBTRIP.y), CREW = coalesce(CREW.x,CREW.y), NOT_FISHED = coalesce(NOT_FISHED.x, NOT_FISHED.y), OPERNUM = coalesce(OPERNUM.x,OPERNUM.y))

Water_yr_merge = subset(Water_yr_merge,select = -c(OPERATOR.x))

Water_yr_merge = subset(Water_yr_merge,select = -c(PERMIT.x))

Water_yr_merge = subset(Water_yr_merge,select = -c(NSUBTRIP.x,CREW.x,NOT_FISHED.x,TRIPCATG.y,OPERATOR.y,OPERNUM.y,PERMIT.y,NSUBTRIP.y,CREW.y,NOT_FISHED.y))

Water_yr_merge <- Water_yr_merge %>% rename(TRIPCATG = TRIPCATG.x)

Water_yr_merge = subset(Water_yr_merge,select = -c(OPERNUM.x))



##Filter out observations from 2020
Water_yr_merge <- Water_yr_merge %>% filter(YEAR != 2020)

```

```{r, echo=FALSE}

```


# Assigning TENMINSQ units to current observations
## 1. Pull in numbered 10-minute squares from Oracle
## 2. Merge 1st year and remaining years from query 
## 3. Merge Complied TENMSQ data with most recent data set (Water_yr_merge_2)

```{r, echo=FALSE}
##SQL Query 

#### Oracle login credentials
oracle_username = "mchaji"
oracle_password = ""
oracle_server = "sole"
ODBC.CONNECTION <- RODBC::odbcConnect(dsn=oracle_server, uid=oracle_username, pwd=oracle_password, believeNRows=FALSE)
START.YEAR = 2007
END.YEAR = 2019
for(i in START.YEAR:END.YEAR) {
    print(i)
    CURRENT.QUERY = paste("SELECT VTR.veslog",i,"g.TENMSQ, TRIPID  
                FROM VTR.veslog",i,"g", sep="")
    FIRST.TENMSQ = sqlQuery(ODBC.CONNECTION, CURRENT.QUERY)  
    
    # Now, the loop compiles the results; the first year must be treated slightly differently###
    if (i==START.YEAR) {
        TENMSQ.COMPILED = FIRST.TENMSQ
    } else {
        TENMSQ.COMPILED = rbind(TENMSQ.COMPILED, FIRST.TENMSQ) }
}    # End Main Loop

## Combine 1st & all other years together 
TENMSQ.all.yrs <- full_join(TENMSQ.COMPILED,FIRST.TENMSQ)

## Join TENMSQ.all.yrs with Water_yr_merge_2
Water_TENMSQ <- merge(Water_yr_merge_2,TENMSQ.all.yrs, by.x = "TRIPID", by.y = "TRIPID", all.x = TRUE, all.y = FALSE)
```





```{r, echo=FALSE}

## Filtered 850 or more and Crew 7 or less
Water_TENMSQ_CREW_LANDED_Filter <- Water_TENMSQ %>% filter(Agg_LANDED >= 850 & CREW <= 8)

##Save CSV





```




##Mapping in clusters 
```{r, echo=FALSE}




leaflet(Water_TENMSQ_CREW_LANDED_Filter) %>%
     addTiles() %>%
    addMarkers(lat = ~DDLAT, lng = ~DDLON, 
                clusterOptions = markerClusterOptions(zoomToBoundsOnClick = T), 
               popup = ~paste(
                    paste('<b>', 'TRIPID:', '</b>', TRIPID), 
                   paste('<b>',  'Aggregated Landings:', '</b>', Agg_LANDED),
                   paste('<b>', 'TENMSQ:', TENMSQ),paste('<b>', 'Year:', YEAR),
                    sep = '<br/>'),
               popupOptions = popupOptions(closeButton = FALSE))







##Read Rasters
All_Lease_Areas <- st_read("~/All_Lease_Areas_Shapefile/All_Lease_Areas.shp")




```




#Import AllJoin0927_TableToExcel Data
## Clean up unneeded columns from data set
```{r, echo=FALSE}
PostArc_10.14$Join_Count <- NULL
PostArc_10.14$Join_Count_1 <- NULL
PostArc_10.14$OID_ <- NULL
PostArc_10.14$TARGET_FID <- NULL
PostArc_10.14$TARGET_FID_1 <- NULL
PostArc_10.14$Field1 <- NULL
PostArc_10.14$Area <- NULL
PostArc_10.14$NOT_FISHED <- NULL
PostArc_10.14$XTXT <- NULL
PostArc_10.14$POINT_X <- NULL
PostArc_10.14$POINT_Y <- NULL
PostArc_10.14$YTXT <- NULL
PostArc_10.14$MN10SQROW <- NULL
PostArc_10.14$MN10SQCOL <- NULL
PostArc_10.14$MN30QUAD <- NULL
PostArc_10.14$MN30SQID <- NULL
PostArc_10.14$DG1SQLAT <- NULL
PostArc_10.14$DG1SQLON <- NULL
PostArc_10.14$DG1SQID <- NULL


#Write Csv
write.csv(PostArc_10.14, "~/R/10.14.Data.csv")


```







```{r}
all_yrs_costs <- merge(X2007_2012,X2013_2020, all = TRUE)
cost_join <- merge(PostArc_10.14,all_yrs_costs, by.x = "TRIPID", by.y = "VTR_TRIPID", all.x = TRUE,all.y =FALSE)

```

#test and check
```{r}
cost_join_10_18 <- cost_join %>% filter(!is.na(TRIP_COST_2020_DOL))
```



