---
title: "Zone Assignment"
author: "Bryce McManus"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
  html_document:
    df_print: paged
    toc: yes
  word_document:
    toc: yes
always_allow_html: true
---
## Intro

This document shows how observations are assigned in FishSET and compares zone
assignments with those found in the most recent version of the scallop data 
(provided Oct/Nov 2021). It then illustrates certain factors that can affect zone 
assignment: polygon boundary types, spherical v. planar geometry, and spatial joins. 

<br><br>

## Library

```{r setup, echo=TRUE, results=FALSE}

# Set Path
here::i_am("scallop_zone_assignment.Rmd")

# Install Packages if necessary and Load Libraries
PKG <- c("here","leaflet", "tidyverse", "sf")
for (p in PKG) {
  if(!require(p,character.only = TRUE)) {
    install.packages(p)
    require(p,character.only = TRUE)}
}

# Set data vintage
vintage_string<-"2022_02_16"
```
   
   
<br><br>

## Data
This is the data from the most recent Kiteworks folder that was shared with the 
FishSET team in Oct/Nov of last year. 
```{r data}
# load in Oct 18 data.
scallop_10_18 <- read_csv(here("data","main","cost_join_10_18.csv"))

# load in final product
final_product_savename<-paste0("final_product_lease",vintage_string,".Rds")
final_product_lease<-readRDS(here("data","main",final_product_savename))

# overwrite 
#scallop_10_18<-final_product_lease

# Load in 10 minute squares
tenMinSqr_new <- 
  here("data",
       "external",
       "shapefiles",
       "Ten Minute Squares Cut North and Greater Atlantic") %>% 
  st_read() %>% 
  st_zm() # remove Z/M dimensions from feature

```
   
<br><br>

Check for duplicate trip IDs. 
```{r}
nrow(scallop_10_18)

scallop_10_18 %>% 
  distinct(TRIPID) %>% 
  nrow()
```
 
    
<br><br>

## Zone assignment

This is the approach we take in FishSET to assign observations to zones.
```{r zone assign}
# create sf version of data, convert to WGS84
# crs <- st_crs(tenMinSqr_new) # using crs from ten minute squares didn't change results
crs <- 4326

scallop_sf <- 
  st_as_sf(x = scallop_10_18, coords = c("DDLON", "DDLAT"), 
           crs = crs)

# convert Squares to WGS84 
tenMinSqr_new <- st_transform(tenMinSqr_new, crs = st_crs(scallop_sf))

# same results as st_within
inter <- sf::st_intersects(scallop_sf, tenMinSqr_new)

inter_save <- inter 
 
 if (any(lengths(inter) > 1)) { # if more than one zone intersects, assign to closest zone
  
  dub <- which(lengths(inter) > 1)
  inter[dub] <- st_nearest_feature(scallop_sf[dub,], tenMinSqr_new)
 }

# Add ZoneID column to data
pts <- as.data.frame(as.numeric(inter))
colnames(pts) <- "col.id"
pts$ID <- tenMinSqr_new$MN10SQID[pts$col.id]
scallop_sf$ZoneID <- pts$ID
```
  
<br><br>
  
52 points did not intersect a zone and 195 intersected multiple zones. The rest
intersected with one zone. Non-intersecting points will show up as `NA` in the 
`ZoneID` column. 
```{r}
table(lengths(inter_save))
```

<br><br>
  
After reassigning zones with 2+ intersections to the nearest zone. 
```{r}
table(lengths(inter))
```
  
<br><br>
  
## FishSET v. NE zone assignment 
Just to recap: `ZoneID` is the zone assignment column created using the FishSET
approach. `MN10SQID` is the zone ID column that came with the updated scallop data.
There is a 6.15% difference (2086 obs) in zone assignments between `ZoneID` and `MN10SQID`.
```{r compare1}
scallop_sf <- scallop_sf %>% 
  mutate(fs_ne_match = ZoneID == MN10SQID)

# add ZoneID and match col to scallop_10_18
scallop_10_18 <- 
  scallop_sf %>% 
  st_set_geometry(NULL) %>% 
  select(ZoneID, fs_ne_match) %>% 
  bind_cols(scallop_10_18, .)

# summary table of matching IDs
scallop_sf %>% 
  st_set_geometry(NULL) %>% 
  summarize(n_obs = n(),
            id_match = sum(fs_ne_match, na.rm = TRUE),
            id_no_match = sum(!fs_ne_match, na.rm = TRUE),
            perc_match = id_match/n() * 100,
            perc_no_match = 100 - perc_match)
```
  
<br><br>
  
All the unassigned points in `ZoneID` fall on a zone intersection.
```{r compare2}
s_bbox <- st_bbox(filter(scallop_sf, is.na(ZoneID)))

ggplot() + 
  geom_sf(data = tenMinSqr_new, fill = "white", color = "black") +
  geom_sf(data = filter(scallop_sf, is.na(ZoneID)),color = "red") +
  coord_sf(xlim = c(s_bbox[1], s_bbox[3]), ylim = c(s_bbox[2], s_bbox[4]))
```

<br><br>
  
The difference in zone assignment appears only to occur on zone boundaries and
intersections.
```{r compare3}
ggplot() +
  geom_sf(data = tenMinSqr_new, fill = "white", color = "black") +
  geom_sf(data = filter(scallop_sf, fs_ne_match),
          aes(color = "Match"), 
          alpha = .2,
          show.legend = "point") +
  geom_sf(data = filter(scallop_sf, !fs_ne_match),
          aes(color = "No match"),
          show.legend = "point") +
  coord_sf(xlim = c(s_bbox[1], s_bbox[3]), ylim = c(s_bbox[2], s_bbox[4])) +
 scale_color_manual(values = c("Match" = "blue", "No match" = "red"))
```
  

<br><br>

This leaflet plot shows the first 20 non-matching zone assignments. Each point
has a label showing the zone assigned by FishSET and by NE. 
```{r compare4}
# marker labels for leaflet plots
scallop_10_18 <- 
  scallop_10_18 %>% 
  mutate(ZoneID_lab = paste0("FS: ", ZoneID, "<br/>"),
         MN10SQID_lab = paste0("NE: ", MN10SQID, "<br/>")) %>% 
  unite("unite_lab", ZoneID_lab, MN10SQID_lab, sep = " ") %>% 
  mutate(unite_lab = paste0(unite_lab, "lon: ", DDLON, "<br/>lat: ", DDLAT))

fs_no_match <- scallop_10_18 %>% 
  filter(fs_ne_match == FALSE) %>% 
  head(20) %>% 
  pull(ZoneID)

ne_no_match <- scallop_10_18 %>% 
  filter(fs_ne_match == FALSE) %>% 
  head(20) %>% 
  pull(MN10SQID)

leaflet() %>%
  addTiles() %>%
  addPolygons(data = filter(tenMinSqr_new, MN10SQID %in% c(fs_no_match, ne_no_match)),
              fillColor = "white",
              fillOpacity = 0.5,
              color = "black",
              stroke = TRUE,
              weight = 1,
              labelOptions = labelOptions(noHide = TRUE),
              layerId = ~MN10SQID,
              label = ~MN10SQID) %>% 
  addMarkers(data = head(filter(scallop_10_18, fs_ne_match == FALSE), 20),
             lng = ~DDLON, lat = ~DDLAT,
             label = ~lapply(unite_lab, htmltools::HTML))
```


<br><br>

Similar to the plot above, but comparing the unassigned points in `ZoneID` with
`MN10SQID`. 
```{r compare5}

if (sum(is.na(scallop_10_18$ZoneID)) > 0) {
  
  fs_na <- scallop_10_18 %>% 
  filter(is.na(ZoneID)) %>% 
  pull(MN10SQID)

leaflet() %>%
  addTiles() %>%
  addPolygons(data = filter(tenMinSqr_new, MN10SQID %in% fs_na),
              fillColor = "white",
              fillOpacity = 0.5,
              color = "black",
              stroke = TRUE,
              weight = 1,
              labelOptions = labelOptions(noHide = TRUE),
              layerId = ~MN10SQID,
              label = ~MN10SQID) %>% 
  addMarkers(data = filter(scallop_10_18, is.na(ZoneID)),
             lng = ~DDLON, lat = ~DDLAT,
             label = ~lapply(unite_lab, htmltools::HTML)) 
}
```

<br><br>

## Factors that may affect point assignment

### Polygon boundary types

Point assignment can vary depending on whether polygon boundaries are treated as 
“closed”, “open”, or “semi-open”.
```{r boundary}
inter_closed <- lengths(st_intersects(scallop_sf, tenMinSqr_new, model = "closed"))
inter_open <- lengths(st_intersects(scallop_sf, tenMinSqr_new, model = "open"))
inter_semi <- lengths(st_intersects(scallop_sf, tenMinSqr_new, model = "semi-open"))

bound_type <- tibble(Closed = inter_closed, Open = inter_open, Semi = inter_semi)

pivot_longer(bound_type, cols = c("Closed", "Open", "Semi"), 
             names_to = "boundary_type", values_to = "Zones_assigned") %>% 
  group_by(boundary_type) %>% 
  count(Zones_assigned)

```

<br><br>

### sf version < 1.0

Sf 1.0+ uses spherical geometry (S2) on coordinates, sf < 1.0 uses planar geometry
(R2). 

```{r r2}
# test difference in S2 and R2 methods
sf_use_s2(FALSE)

inter_closed_r2 <- lengths(st_intersects(scallop_sf, tenMinSqr_new, model = "closed"))
inter_open_r2 <- lengths(st_intersects(scallop_sf, tenMinSqr_new, model = "open"))
inter_semi_r2 <- lengths(st_intersects(scallop_sf, tenMinSqr_new, model = "semi-open"))

sf_use_s2(TRUE)

bound_type_r2 <- tibble(Closed = inter_closed_r2, 
                        Open = inter_open_r2, 
                        Semi = inter_semi_r2)

pivot_longer(bound_type_r2, cols = c("Closed", "Open", "Semi"), 
             names_to = "boundary_type", values_to = "Zones_assigned") %>% 
  group_by(boundary_type) %>% 
  count(Zones_assigned)

```

<br><br>

### Spatial join

Spatial joins will add additional rows if a point intersects more than one zone.
If an inner join is used (`left = FALSE`), points that don't intersect zones are dropped.

```{r join1}

scallop_sf_join <- st_join(scallop_sf, 
                           tenMinSqr_new["MN10SQID"], 
                           suffix = c(".x", ".y"),
                           left = TRUE)

scallop_sf_join <- 
  scallop_sf_join %>%
  mutate(fs_join_match = ZoneID == MN10SQID.y,
         ne_join_match = MN10SQID.x == MN10SQID.y)

scallop_sf_join %>% 
  st_set_geometry(NULL) %>% 
  summarize(n_obs = n(),
    fs_join_match = sum(fs_join_match, na.rm = TRUE),
    ne_join_match = sum(ne_join_match, na.rm = TRUE), 
    fs_ne_match = sum(fs_ne_match, na.rm = TRUE))
```

<br><br>

Spatial join adds 195 rows: one for each point that intersected two zones. 

```{r join2}
nrow(scallop_sf_join)

scallop_sf_join %>% 
  st_set_geometry(NULL) %>% 
  distinct(TRIPID) %>% 
  nrow()
```

<br><br>

Table of matching zones by FishSET, NE, and spatial join approaches. 
```{r}
scallop_sf_join %>% 
    st_set_geometry(NULL) %>% 
    count(fs_ne_match, fs_join_match, ne_join_match)
```

<br> 
All 195 of the cases from the first row of the table above (no shared zone assignments)
are from points assigned to multiple zones. No approach handled this 
case in the same way. 
```{r}
dup_trip_id <- scallop_10_18$TRIPID[lengths(inter_save) > 1]

scallop_sf_join <- 
  scallop_sf_join %>% 
  mutate(dup_zone = TRIPID %in% dup_trip_id)

scallop_sf_join %>% 
  st_set_geometry(NULL) %>% 
  filter(!fs_ne_match & !fs_join_match & !ne_join_match) %>% 
  summarize(dup_zone = sum(dup_zone))
```

