---
title: "case_study_comparisons"
author: "Marina Chaji"
date: "2024-01-19"
output: html_document
---

params:
  AA_DAS_only: no
---

```{r}

#save to RDS
rds_savename<-paste0("Inside_CA1_",vintage_string,".Rds")
csv_savename<-paste0("Inside_CA1_",vintage_string,".csv")


saveRDS(Inside_CA1, file=here("data","main",rds_savename))
write.csv(Inside_CA1,file=here("data","main",csv_savename), row.names = FALSE)


```


GC-IFQ
```{r}

## New York Bight 

Inside_CA1 <- scallop0322MainDataTable_CA1_2023_11_06 %>% filter(in_closure == "TRUE")

#Inside_CA2 <- scallop0322MainDataTable_CA2_2023_11_06 %>% filter(in_closure == "TRUE")

#Inside_CA3 <- scallop0322MainDataTable_CA3_2023_11_06 %>% filter(in_closure == "TRUE")


#dropped_values_CA_1_2 <- anti_join(Inside_CA1, Inside_CA2, by = c("TRIPID" = "TRIPID"))

#dropped_values_CA_2_3 <- anti_join(Inside_CA2, Inside_CA3, by = c("TRIPID" = "TRIPID"))



## Central AtLAntic 

#Inside_CA1_GC <- scallop0322MainDataTable %>% filter(in_closure == "TRUE")

#Inside_CA2_GC <- scallop0322MainDataTable %>% filter(in_closure == "TRUE")

#Inside_CA3_GC <- scallop0322MainDataTable %>% filter(in_closure == "TRUE")

dropped_values_CA_1_2_GC <- anti_join(Inside_CA1_GC, Inside_CA2_GC, by = c("TRIPID" = "TRIPID"))

dropped_values_CA_2_3_GC <- anti_join(Inside_CA2_GC, Inside_CA3_GC, by = c("TRIPID" = "TRIPID"))

```


Limited Access
```{r}

## New York Bight 

Inside_CA1_LA <- scallop0322MainDataTable %>% filter(in_closure == "TRUE")

Inside_CA2_LA <- scallop0322MainDataTable %>% filter(in_closure == "TRUE")

Inside_CA3_LA <- scallop0322MainDataTable %>% filter(in_closure == "TRUE")


dropped_values_CA_1_2_LA <- anti_join(Inside_CA1_LA, Inside_CA2_LA, by = c("TRIPID" = "TRIPID"))

dropped_values_CA_2_3_LA <- anti_join(Inside_CA2_LA, Inside_CA3_LA, by = c("TRIPID" = "TRIPID"))



## Central AtLAntic 

#Inside_CA1_LA <- scallop0322MainDataTable %>% filter(in_closure == "TRUE")

#Inside_CA2_LA <- scallop0322MainDataTable %>% filter(in_closure == "TRUE")

#Inside_CA3_LA <- scallop0322MainDataTable %>% filter(in_closure == "TRUE")

dropped_values_CA_1_2_LA <- anti_join(Inside_CA1_LA, Inside_CA2_LA, by = c("TRIPID" = "TRIPID"))

dropped_values_CA_2_3_LA <- anti_join(Inside_CA2_LA, Inside_CA3_LA, by = c("TRIPID" = "TRIPID"))

```



```{r}

## New York Bight

#if (params$AA_DAS_only==TRUE){
 Inside_CA1_AA <- Inside_CA1_LA %>% filter(fleet == "Access Area") 
 Inside_CA1_DAS <- Inside_CA1_LA %>% filter(fleet == "Days at Sea") 
 
 Inside_CA2_AA <- Inside_CA2_LA %>% filter(fleet == "Access Area") 
 Inside_CA2_DAS <- Inside_CA2_LA %>% filter(fleet == "Days at Sea") 
 
 Inside_CA3_AA <- Inside_CA3_LA %>% filter(fleet == "Access Area") 
 Inside_CA3_DAS <- Inside_CA3_LA %>% filter(fleet == "Days at Sea") 
 
 
 dropped_values_CA_1_2_AA <- dropped_values_CA_1_2_LA %>% filter(fleet == "Access Area") 
 dropped_values_CA_1_2_DAS <- dropped_values_CA_1_2_LA %>% filter(fleet == "Days at Sea") 
 
 dropped_values_CA_2_3_AA <- dropped_values_CA_2_3_LA %>% filter(fleet == "Access Area") 
 dropped_values_CA_2_3_DAS <- dropped_values_CA_2_3_LA %>% filter(fleet == "Days at Sea") 

# }


## Central Atlantic


Inside_CA1_AA <- Inside_CA1_LA %>% filter(fleet == "Access Area") 
Inside_CA1_DAS <- Inside_CA1_LA %>% filter(fleet == "Days at Sea") 
 
Inside_CA2_AA <- Inside_CA2_LA %>% filter(fleet == "Access Area") 
Inside_CA2_DAS <- Inside_CA2_LA %>% filter(fleet == "Days at Sea") 
 
Inside_CA3_AA <- Inside_CA3_LA %>% filter(fleet == "Access Area") 
Inside_CA3_DAS <- Inside_CA3_LA %>% filter(fleet == "Days at Sea") 
 
 
dropped_values_CA_1_2_AA <- dropped_values_CA_1_2_LA %>% filter(fleet == "Access Area") 
dropped_values_CA_1_2_DAS <- dropped_values_CA_1_2_LA %>% filter(fleet == "Days at Sea") 
 
dropped_values_CA_2_3_AA <- dropped_values_CA_2_3_LA %>% filter(fleet == "Access Area") 
dropped_values_CA_2_3_DAS <- dropped_values_CA_2_3_LA %>% filter(fleet == "Days at Sea") 


```


# Save Data 
```{r}
save(Inside_CA1, Inside_CA2,Inside_CA3, file = "compare_data.RData")
# To load the data again
#load("compare_data.RData")

```

<br><br><br> 

# Average Winsorized Revenue in closures GC-IFQ

```{r}

zone_out <- 
zone_summary(dropped_values_CA_1_2_GC, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "DOLLAR_2022_win",
         fun = "mean",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```

```{r}

zone_out <- 
zone_summary(dropped_values_CA_2_3_GC, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "DOLLAR_2022_win",
         fun = "mean",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```


<br><br><br>


# Average Winsorized Revenue in closures by fleet LA 

```{r}

zone_out <- 
zone_summary(dropped_values_CA_1_2_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "DOLLAR_2022_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```


```{r}

zone_out <- 
zone_summary(dropped_values_CA_2_3_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "DOLLAR_2022_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```



<br><br><br>

GC-IFQ Testing 
```{r}

BSDA::z.test(dropped_values_1_2$DOLLAR_2022_win,
  y = Inside_CA2$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_1_2$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_1_2$DOLLAR_2022_win,
  y = Inside_CA2$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_1_2$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_1_2$DOLLAR_2022_win,
  y = Inside_CA2$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_1_2$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

```


Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```



```

<br><br><br>




Average winsorized Landed in closures

```{r}

zone_out <- 
zone_summary(dropped_values_CA_1_2_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "LANDED_win",
         fun = "mean",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```



<br><br><br> <br><br><br>

Average winsorized Landed in closures by fleet

```{r}

zone_out <- 
zone_summary(dropped_values_CA_1_2_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "LANDED_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```

```{r}

zone_out <- 
zone_summary(dropped_values_CA_2_3_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "LANDED_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```

<br><br><br>
GC-IFQ z-tests
```{r}

BSDA::z.test(dropped_values_2_3$LANDED_win,
  y = Inside_CA2$LANDED_win,
  sigma.x = sd(dropped_values_2_3$LANDED_win),
  sigma.y = sd(Inside_CA2$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_2_3$LANDED_win,
  y = Inside_CA2$LANDED_win,
  sigma.x = sd(dropped_values_2_3$LANDED_win),
  sigma.y = sd(Inside_CA2$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)

BSDA::z.test(dropped_values_2_3$LANDED_win,
  y = Inside_CA2$LANDED_win,
  sigma.x = sd(dropped_values_2_3$LANDED_win),
  sigma.y = sd(Inside_CA2$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


```


<br><br><br>





Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```


<br><br><br> 

Average Winsorized Operating Profit by closure area.

```{r}
zone_out <- 
zone_summary(dropped_values_2_3, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "OPERATING_PROFIT_2022_win",
         fun = "mean",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = TRUE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "60%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
zone_out$plot }

```


<br><br><br> Average Winsorized Operating Profit in closures by fleet

```{r}
zone_out <- 
zone_summary(dropped_values_CA_1_2_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "OPERATING_PROFIT_2022_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = TRUE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}


```

```{r}
zone_out <- 
zone_summary(dropped_values_CA_2_3_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "OPERATING_PROFIT_2022_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = TRUE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```



<br><br><br>


```{r}
BSDA::z.test(dropped_values_2_3$OPERATING_PROFIT_2022_win,
  y = Inside_CA2$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_2_3$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_2_3$OPERATING_PROFIT_2022_win,
  y = Inside_CA2$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_2_3$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_2_3$OPERATING_PROFIT_2022_win,
  y = Inside_CA2$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_2_3$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)
```


<br><br><br>

Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```




<br><br><br>

Average winsorized VPUE in closures

```{r}

zone_out <- 
zone_summary(dropped_values_2_3, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "VPUE_win",
         fun = "mean",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```



<br><br><br> <br><br><br>

Average winsorized VPUE in closures by fleet

```{r}

zone_out <- 
zone_summary(dropped_values_CA_1_2_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "VPUE_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```


```{r}

zone_out <- 
zone_summary(dropped_values_CA_2_3_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "VPUE_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```



<br><br><br>

```{r}

BSDA::z.test(dropped_values_1_2$VPUE_win,
  y = Inside_CA2$VPUE_win,
  sigma.x = sd(dropped_values_1_2$VPUE_win),
  sigma.y = sd(Inside_CA2$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_1_2$VPUE_win,
  y = Inside_CA2$VPUE_win,
  sigma.x = sd(dropped_values_1_2$VPUE_win),
  sigma.y = sd(Inside_CA2$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_1_2$VPUE_win,
  y = Inside_CA2$VPUE_win,
  sigma.x = sd(dropped_values_1_2$VPUE_win),
  sigma.y = sd(Inside_CA2$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

```

<br><br><br>


<br><br><br>
Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```
<br><br><br> 



# Central Atlantic Comparisons


## Average Winsorized Revenue in closures GC-IFQ

```{r}

zone_out <- 
zone_summary(dropped_values_CA_1_2_GC, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "DOLLAR_2022_win",
         fun = "mean",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```

```{r}

zone_out <- 
zone_summary(dropped_values_CA_2_3_GC, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "DOLLAR_2022_win",
         fun = "mean",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```


<br><br><br>


# Average Winsorized Revenue in closures by fleet LA 

```{r}

zone_out <- 
zone_summary(dropped_values_CA_1_2_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "DOLLAR_2022_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```


```{r}

zone_out <- 
zone_summary(dropped_values_CA_2_3_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "DOLLAR_2022_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```



<br><br><br>

GC-IFQ Testing 
```{r}

BSDA::z.test(dropped_values_1_2$DOLLAR_2022_win,
  y = Inside_CA2$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_1_2$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_1_2$DOLLAR_2022_win,
  y = Inside_CA2$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_1_2$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_1_2$DOLLAR_2022_win,
  y = Inside_CA2$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_1_2$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

```


Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```



```

<br><br><br>




Average winsorized Landed in closures

```{r}

zone_out <- 
zone_summary(dropped_values_CA_1_2_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "LANDED_win",
         fun = "mean",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```



<br><br><br> <br><br><br>

Average winsorized Landed in closures by fleet

```{r}

zone_out <- 
zone_summary(dropped_values_CA_1_2_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "LANDED_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```

```{r}

zone_out <- 
zone_summary(dropped_values_CA_2_3_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "LANDED_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```

<br><br><br>
GC-IFQ z-tests
```{r}

BSDA::z.test(dropped_values_CA_2_3_GC$LANDED_win,
  y = Inside_CA2_GC$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_GC$LANDED_win),
  sigma.y = sd(Inside_CA2_GC$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_CA_2_3_GC$LANDED_win,
  y = Inside_CA2_GC$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_GC$LANDED_win),
  sigma.y = sd(Inside_CA2_GC$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)

BSDA::z.test(dropped_values_CA_2_3_GC$LANDED_win,
  y = Inside_CA2_GC$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_GC$LANDED_win),
  sigma.y = sd(Inside_CA2_GC$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


```


<br><br><br>





Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```


<br><br><br> 

Average Winsorized Operating Profit by closure area.

```{r}
zone_out <- 
zone_summary(dropped_values_CA_1_2_GC, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "OPERATING_PROFIT_2022_win",
         fun = "mean",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = TRUE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "60%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
zone_out$plot }

```
<br><br><br> 

Average Winsorized Operating Profit by closure area.

```{r}
zone_out <- 
zone_summary(dropped_values_CA_2_3_GC, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "OPERATING_PROFIT_2022_win",
         fun = "mean",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = TRUE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "60%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
zone_out$plot }

```

<br><br><br> Average Winsorized Operating Profit in closures by fleet

```{r}
zone_out <- 
zone_summary(dropped_values_CA_1_2_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "OPERATING_PROFIT_2022_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = TRUE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}


```

```{r}
zone_out <- 
zone_summary(dropped_values_CA_2_3_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "OPERATING_PROFIT_2022_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = TRUE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```



<br><br><br>

##GCIFQ Test 

```{r}
# Phase 1 to 2 
BSDA::z.test(dropped_values_CA_1_2_GC$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_CA_1_2_GC$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_GC$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Phase 2 to 3 

BSDA::z.test(dropped_values_CA_2_3_GC$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_CA_2_3_GC$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_GC$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)
```


<br><br><br>

Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_GC_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_GC_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_GC_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_GC_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_GC_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_GC_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_GC_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_GC_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_GC_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_GC_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_GC_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA3_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_GC_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_GC_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_GC_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_GC_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_GC_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_GC_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_GC_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_GC_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_GC_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_GC_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_GC_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_GC_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_GC_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```




<br><br><br>

Average winsorized VPUE in closures

```{r}

zone_out <- 
zone_summary(dropped_values_CA_2_3, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "VPUE_win",
         fun = "mean",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```



<br><br><br> <br><br><br>

Average winsorized VPUE in closures by fleet

```{r}

zone_out <- 
zone_summary(dropped_values_CA_1_2_GC_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "VPUE_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```


```{r}

zone_out <- 
zone_summary(dropped_values_CA_2_3_GC_LA, project = project,
         spat = scallop0322WindCloseSpatTable,
         zone.dat = "closeID",
         zone.spat = "LEASE_NUMB",
         var = "VPUE_win",
         fun = "mean",
         group = "fleet",
         count = FALSE, 
         breaks = c(.001, .01, .1, .3, .5, .7),
         na.rm = FALSE, dat.center = FALSE,
         output = out_switch)

if (out_switch == "table") {
  eval_next=FALSE
  zone_out %>% 
    pretty_lab() %>% 
    pretty_tab_sb(width = "40%")
  
} else if (out_switch=="tab_plot"){
  eval_next=TRUE
  zone_out$plot
}

```



<br><br><br>

```{r}

BSDA::z.test(dropped_values_1_2$VPUE_win,
  y = Inside_CA2$VPUE_win,
  sigma.x = sd(dropped_values_1_2$VPUE_win),
  sigma.y = sd(Inside_CA2$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_1_2$VPUE_win,
  y = Inside_CA2$VPUE_win,
  sigma.x = sd(dropped_values_1_2$VPUE_win),
  sigma.y = sd(Inside_CA2$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_1_2$VPUE_win,
  y = Inside_CA2$VPUE_win,
  sigma.x = sd(dropped_values_1_2$VPUE_win),
  sigma.y = sd(Inside_CA2$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

```

<br><br><br>


<br><br><br>
Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_GC_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_GC_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_GC_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_GC_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_GC_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_GC_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_GC_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_GC_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_GC_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_GC_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_GC_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_GC_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_GC_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_GC_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_GC_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_GC_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_GC_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_GC_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_GC_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_GC_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_GC_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_GC_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_GC_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_GC_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```
