---
title: "case_study_comparisons"
author: "Marina Chaji"
date: "2024-01-19"
output: html_document
---


## About 
 
This report uses data sets from the tiny reports to estimate based on our five key metrics: trips, ex-vessel scallop revenue, scallop landings, operating profit, and revenue per day across the Limited Access and General Category-IFQ fleets. The Limited Access fleet is characterized by metiers, Access Area (AA) & Days-at-Sea(DAS). We also test for equality of means in areas excluded as regulatory processes occur using z-tests between phases, i.e., Call Area(s) to Wind Energy Area(s) and Wind Energy Area(s) to Lease Area(s) in the New York Bight (NY) & Central Atlantic (CA) regions. 


```{r setup, echo=FALSE}

library(FishSET)
library(BSDA) # z-tests 
library(plyr)
library(dplyr)
library(readr)
library(knitr) #creates tables when knitting 
library(here)

here::i_am("analysis_code/case_study_comparisons.Rmd")
# helper functions
source(here("analysis_code", "format_helpers.R"))

project <- "scallop0322"
pounds_to_kg<-2.20462
# disable scientific notation
options(scipen=999)

#load in data here The data sets used in this rmd are sourced from tiny reports after closure assignment using FishSET. Each should be categorized by shapefile name i.e. "Central Atlantic (CA)" and fleet type. All necessary data for this rmd can be loaded below and is updated as of January 31st 2024. Otherwise the chunk below can be used to create a new updated .RData file to use. 

# load("~/mchaji_net/READ-SSB-CHAJI-Effort-Displacement---Scallop/data/main/comparisons/comparasion_data_ALL.RData")



```




```{r}


#Load GCIFQ data 

NY1_GC <- readRDS(here::here("data","main","casestudies","casestudy_gc_NY1_2023_11_06.Rds"))
NY2_GC <- readRDS(here::here("data","main","casestudies","casestudy_gc_NY2_2023_11_06.Rds"))
NY3_GC <- readRDS(here::here("data","main","casestudies","casestudy_gc_NY3_2023_11_06.Rds"))

CA1_GC <- readRDS(here::here("data","main","casestudies","casestudy_gc_CA1_2023_11_06.Rds"))
CA2_GC <- readRDS(here::here("data","main","casestudies","casestudy_gc_CA2_2023_11_06.Rds"))
CA3_GC <- readRDS(here::here("data","main","casestudies","casestudy_gc_CA3_2023_11_06.Rds"))



#Load LA data 


NY1_LA <- readRDS(here::here("data","main","casestudies","casestudy_LA_NY1_2023_11_06.Rds"))
NY2_LA <- readRDS(here::here("data","main","casestudies","casestudy_LA_NY2_2023_11_06.Rds"))
NY3_LA <- readRDS(here::here("data","main","casestudies","casestudy_LA_NY3_2023_11_06.Rds"))

CA1_LA <- readRDS(here::here("data","main","casestudies","casestudy_LA_CA1_2023_11_06.Rds"))
CA2_LA <- readRDS(here::here("data","main","casestudies","casestudy_LA_CA2_2023_11_06.Rds"))
CA3_LA <- readRDS(here::here("data","main","casestudies","casestudy_LA_CA3_2023_11_06.Rds"))

```


GC-IFQ
```{r}

## New York Bight 

Inside_NY1_GC <- NY1_GC %>% filter(in_closure == "TRUE")

Inside_NY2_GC <- NY2_GC %>% filter(in_closure == "TRUE")

Inside_NY3_GC <- NY3_GC %>% filter(in_closure == "TRUE")


dropped_values_NY_1_2_GC <- anti_join(Inside_NY1_GC, Inside_NY2_GC, by = c("TRIPID" = "TRIPID"))

dropped_values_NY_2_3_GC <- anti_join(Inside_NY2_GC, Inside_NY3_GC, by = c("TRIPID" = "TRIPID"))



## Central Atlantic 

Inside_CA1_GC <- CA1_GC %>% filter(in_closure == "TRUE")

Inside_CA2_GC <- CA2_GC %>% filter(in_closure == "TRUE")

Inside_CA3_GC <- CA3_GC %>% filter(in_closure == "TRUE")


dropped_values_CA_1_2_GC <- anti_join(Inside_CA1_GC, Inside_CA2_GC, by = c("TRIPID" = "TRIPID"))

dropped_values_CA_2_3_GC <- anti_join(Inside_CA2_GC, Inside_CA3_GC, by = c("TRIPID" = "TRIPID"))

dropped_values_CA_1_3_GC <- anti_join(Inside_CA1_GC, Inside_CA3_GC, by = c("TRIPID" = "TRIPID"))


```


Limited Access
```{r}

## New York Bight 

Inside_NY1_LA <- NY1_LA %>% filter(in_closure == "TRUE")

Inside_NY2_LA <- NY2_LA %>% filter(in_closure == "TRUE")

Inside_NY3_LA <- NY3_LA %>% filter(in_closure == "TRUE")


dropped_values_NY_1_2_LA <- anti_join(Inside_NY1_LA, Inside_NY2_LA, by = c("TRIPID" = "TRIPID"))

dropped_values_NY_2_3_LA <- anti_join(Inside_NY2_LA, Inside_NY3_LA, by = c("TRIPID" = "TRIPID"))



## Central Atlantic 

Inside_CA1_LA <- CA1_LA %>% filter(in_closure == "TRUE")

Inside_CA2_LA <- CA2_LA %>% filter(in_closure == "TRUE")

Inside_CA3_LA <- CA3_LA %>% filter(in_closure == "TRUE")


dropped_values_CA_1_2_LA <- anti_join(Inside_CA1_LA, Inside_CA2_LA, by = c("TRIPID" = "TRIPID"))

dropped_values_CA_2_3_LA <- anti_join(Inside_CA2_LA, Inside_CA3_LA, by = c("TRIPID" = "TRIPID"))

dropped_values_CA_1_3_LA <- anti_join(Inside_CA1_LA, Inside_CA3_LA, by = c("TRIPID" = "TRIPID"))

```

```{r}
#tests
view_lon_lat(Inside_CA2_LA, lon = "DDLON", lat ="DDLAT")
view_lon_lat(dropped_values_NY_2_3_LA, lon = "DDLON", lat ="DDLAT")
view_lon_lat(Inside_CA3_LA, lon = "DDLON", lat ="DDLAT")

```

```{r}

## New York Bight


 Inside_NY1_AA <- Inside_CA1_LA %>% filter(fleet == "Access Area") 
 Inside_CA1_DAS <- Inside_CA1_LA %>% filter(fleet == "Days at Sea") 
 
 Inside_NY2_AA <- Inside_CA2_LA %>% filter(fleet == "Access Area") 
 Inside_NY2_DAS <- Inside_CA2_LA %>% filter(fleet == "Days at Sea") 
 
 Inside_NY3_AA <- Inside_CA3_LA %>% filter(fleet == "Access Area") 
 Inside_NY3_DAS <- Inside_CA3_LA %>% filter(fleet == "Days at Sea") 
 
 
 dropped_values_NY_1_2_AA <- dropped_values_NY_1_2_LA %>% filter(fleet == "Access Area") 
 dropped_values_NY_1_2_DAS <- dropped_values_NY_1_2_LA %>% filter(fleet == "Days at Sea") 
 
 dropped_values_NY_2_3_AA <- dropped_values_NY_2_3_LA %>% filter(fleet == "Access Area") 
 dropped_values_NY_2_3_DAS <- dropped_values_NY_2_3_LA %>% filter(fleet == "Days at Sea") 

 
 dropped_values_NY_1_3_AA <- dropped_values_NY_1_2_LA %>% filter(fleet == "Access Area") 
 dropped_values_NY_1_3_DAS <- dropped_values_NY_1_2_LA %>% filter(fleet == "Days at Sea") 



## Central Atlantic


Inside_CA1_AA <- Inside_CA1_LA %>% filter(fleet == "Access Area") 
Inside_CA1_DAS <- Inside_CA1_LA %>% filter(fleet == "Days at Sea") 
 
Inside_CA2_AA <- Inside_CA2_LA %>% filter(fleet == "Access Area") 
Inside_CA2_DAS <- Inside_CA2_LA %>% filter(fleet == "Days at Sea") 
 
Inside_CA3_AA <- Inside_CA3_LA %>% filter(fleet == "Access Area") 
Inside_CA3_DAS <- Inside_CA3_LA %>% filter(fleet == "Days at Sea") 
 
 
dropped_values_CA_1_2_AA <- dropped_values_CA_1_2_LA %>% filter(fleet == "Access Area") 
dropped_values_CA_1_2_DAS <- dropped_values_CA_1_2_LA %>% filter(fleet == "Days at Sea") 
 
dropped_values_CA_2_3_AA <- dropped_values_CA_2_3_LA %>% filter(fleet == "Access Area") 
dropped_values_CA_2_3_DAS <- dropped_values_CA_2_3_LA %>% filter(fleet == "Days at Sea") 

dropped_values_CA_1_3_AA <- dropped_values_CA_1_3_LA %>% filter(fleet == "Access Area") 
dropped_values_CA_1_3_DAS <- dropped_values_CA_1_3_LA %>% filter(fleet == "Days at Sea") 



```



# Save Data 
```{r}
# This set is only necessary if using a new data set

#save(CA1_GC, CA2_GC,CA3_GC,NY1_GC,NY2_GC,NY3_GC, CA1_LA, CA2_LA,CA3_LA, NY1_LA,NY2_LA,NY3_LA ,file = "~/mchaji_net/READ-SSB-CHAJI-Effort-Displacement---Scallop/data/main/comparisons/comparasion_data_ALL.RData")


```

<br><br><br> 

# Central Atlantic Section 


# Aggregate Scallop Revenue and Operating Profit CA1, CA2, and CA3 and the Dropped Values from 1-3 for the LA Fleet

```{r}
 Inside_CA1_LA %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=sum(DOLLAR_2022_win),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))


Inside_CA2_LA %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=sum(DOLLAR_2022_win),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))

Inside_CA3_LA %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=sum(DOLLAR_2022_win),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))



dropped_values_CA_1_3_LA %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=sum(DOLLAR_2022_win),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))

```


##  Average Revenue, VPUE, Operating Profit, and  Landed weights for the Central Atlantic, GCIFQ

```{r}

dropped_values_CA_1_3_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=mean(DOLLAR_2022_win),VPUE_win=mean(VPUE_win),
                   LANDED_win=mean(LANDED_win), OPERATING_win=mean(OPERATING_PROFIT_2022_win))


dropped_values_CA_1_2_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=mean(DOLLAR_2022_win),VPUE_win=mean(VPUE_win),
                   LANDED_win=mean(LANDED_win), OPERATING_win=mean(OPERATING_PROFIT_2022_win))


dropped_values_CA_2_3_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=mean(DOLLAR_2022_win),VPUE_win=mean(VPUE_win),
                   LANDED_win=mean(LANDED_win), OPERATING_win=mean(OPERATING_PROFIT_2022_win))


```


<br><br><br>


# Average Winsorized Revenue, VPUE, Operating Profit, and Landings in CA closures by fleet LA 


```{r}

dropped_values_CA_1_3_LA %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=mean(DOLLAR_2022_win),VPUE_win=mean(VPUE_win),
                   LANDED_win=mean(LANDED_win), OPERATING_win=mean(OPERATING_PROFIT_2022_win))


dropped_values_CA_1_2_LA %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=mean(DOLLAR_2022_win),VPUE_win=mean(VPUE_win),
                   LANDED_win=mean(LANDED_win), OPERATING_win=mean(OPERATING_PROFIT_2022_win))


dropped_values_CA_2_3_LA %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=mean(DOLLAR_2022_win),VPUE_win=mean(VPUE_win),
                   LANDED_win=mean(LANDED_win), OPERATING_win=mean(OPERATING_PROFIT_2022_win))


```

<br><br><br>
# Aggregate Scallop revenue CA1, CA2, and CA3 and the Dropped Values from 1-3 for the GCIFQ Fleet

```{r}


Inside_CA1_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=sum(DOLLAR_2022),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))


Inside_CA2_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=sum(DOLLAR_2022),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))

Inside_CA3_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=sum(DOLLAR_2022),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))



dropped_values_CA_1_3_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=sum(DOLLAR_2022),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))

```
<br><br><br>


CA GC-IFQ Testing 
```{r}

BSDA::z.test(dropped_values_CA_1_3_GC$DOLLAR_2022_win,
  y = Inside_CA3_GC$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_GC$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA3_GC$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_3_GC$DOLLAR_2022_win,
  y = Inside_CA3_GC$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_GC$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA3_GC$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_3_GC$DOLLAR_2022_win,
  y = Inside_CA3_GC$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_GC$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA3_GC$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

```


Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_AA$DOLLAR_2022_win,
  y = Inside_CA2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 1 to 3

BSDA::z.test(dropped_values_CA_1_3_AA$DOLLAR_2022_win,
  y = Inside_CA3_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA3_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_3_AA$DOLLAR_2022_win,
  y = Inside_CA3_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA3_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_3_AA$DOLLAR_2022_win,
  y = Inside_CA3_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA3_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_DAS$DOLLAR_2022_win,
  y = Inside_CA2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 1 to 3

BSDA::z.test(dropped_values_CA_1_3_DAS$DOLLAR_2022_win,
  y = Inside_CA3_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA3_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_3_DAS$DOLLAR_2022_win,
  y = Inside_CA3_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA3_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_3_DAS$DOLLAR_2022_win,
  y = Inside_CA3_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_CA3_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

```



```

<br><br><br>





<br><br><br>
GC-IFQ z-tests
```{r}

BSDA::z.test(dropped_values_CA_1_3_GC$LANDED_win,
  y = Inside_CA3_GC$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_3_GC$LANDED_win),
  sigma.y = sd(Inside_CA3_GC$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_CA_1_3_GC$LANDED_win,
  y = Inside_CA3_GC$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_3_GC$LANDED_win),
  sigma.y = sd(Inside_CA3_GC$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)

BSDA::z.test(dropped_values_CA_1_3_GC$LANDED_win,
  y = Inside_CA3_GC$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_3_GC$LANDED_win),
  sigma.y = sd(Inside_CA3_GC$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


```


<br><br><br>





Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_AA$LANDED_win,
  y = Inside_CA2_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$LANDED_win),
  sigma.y = sd(Inside_CA2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 1 to 3
BSDA::z.test(dropped_values_CA_1_3_AA$LANDED_win,
  y = Inside_CA3_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_3_AA$LANDED_win),
  sigma.y = sd(Inside_CA3_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_3_AA$LANDED_win,
  y = Inside_CA3_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_3_AA$LANDED_win),
  sigma.y = sd(Inside_CA3_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_3_AA$LANDED_win,
  y = Inside_CA3_AA$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_3_AA$LANDED_win),
  sigma.y = sd(Inside_CA3_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_DAS$LANDED_win,
  y = Inside_CA2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$LANDED_win),
  sigma.y = sd(Inside_CA2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 1 to 3
BSDA::z.test(dropped_values_CA_1_3_DAS$LANDED_win,
  y = Inside_CA3_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_3_DAS$LANDED_win),
  sigma.y = sd(Inside_CA3_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_3_DAS$LANDED_win,
  y = Inside_CA3_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_3_DAS$LANDED_win),
  sigma.y = sd(Inside_CA3_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_3_DAS$LANDED_win,
  y = Inside_CA3_DAS$LANDED_win,
  sigma.x = sd(dropped_values_CA_1_3_DAS$LANDED_win),
  sigma.y = sd(Inside_CA3_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```

 

<br><br><br>
GCIFQ z-tests

```{r}
BSDA::z.test(dropped_values_CA_2_3_GC$OPERATING_PROFIT_2022_win,
  y = Inside_CA3_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_CA_2_3_GC$OPERATING_PROFIT_2022_win,
  y = Inside_CA3_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_GC$OPERATING_PROFIT_2022_win,
  y = Inside_CA3_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)
```


<br><br><br>

Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 1 to 3
BSDA::z.test(dropped_values_CA_1_3_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA3_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_3_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA3_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_3_AA$OPERATING_PROFIT_2022_win,
  y = Inside_CA3_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 1 to 3
BSDA::z.test(dropped_values_CA_1_3_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA3_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_3_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA3_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_3_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_CA3_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_CA_1_3_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_CA3_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)




```


<br><br><br>
GCIFQ z-tests
```{r}

BSDA::z.test(dropped_values_CA_1_3_GC$VPUE_win,
  y = Inside_CA3_GC$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_3_GC$VPUE_win),
  sigma.y = sd(Inside_CA3_GC$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_3_GC$VPUE_win,
  y = Inside_CA3_GC$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_3_GC$VPUE_win),
  sigma.y = sd(Inside_CA3_GC$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_3_GC$VPUE_win,
  y = Inside_CA3_GC$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_3_GC$VPUE_win),
  sigma.y = sd(Inside_CA3_GC$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

```

<br><br><br>


<br><br><br>
Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_AA$VPUE_win,
  y = Inside_CA2_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_AA$VPUE_win),
  sigma.y = sd(Inside_CA2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 1 to 3
BSDA::z.test(dropped_values_CA_1_3_AA$VPUE_win,
  y = Inside_CA3_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_3_AA$VPUE_win),
  sigma.y = sd(Inside_CA3_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_3_AA$VPUE_win,
  y = Inside_CA3_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_3_AA$VPUE_win),
  sigma.y = sd(Inside_CA3_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_3_AA$VPUE_win,
  y = Inside_CA3_AA$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_3_AA$VPUE_win),
  sigma.y = sd(Inside_CA3_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)




# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_CA_1_2_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_2_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_2_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_2_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_CA_2_3_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_2_3_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_2_3_DAS$VPUE_win,
  y = Inside_CA2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_2_3_DAS$VPUE_win),
  sigma.y = sd(Inside_CA2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 1 to 3
BSDA::z.test(dropped_values_CA_1_3_DAS$VPUE_win,
  y = Inside_CA3_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_3_DAS$VPUE_win),
  sigma.y = sd(Inside_CA3_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_CA_1_3_DAS$VPUE_win,
  y = Inside_CA3_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_3_DAS$VPUE_win),
  sigma.y = sd(Inside_CA3_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_CA_1_3_DAS$VPUE_win,
  y = Inside_CA3_DAS$VPUE_win,
  sigma.x = sd(dropped_values_CA_1_3_DAS$VPUE_win),
  sigma.y = sd(Inside_CA3_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)





```
<br><br><br> 



# New York Bight (NY) Comparisons


# Aggregate Scallop revenue and Operating Profit by NY 1, 2, and 3 and dropped values. GC fleet
Total revenue and operating profits
```{r}
 

 Inside_NY1_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=sum(DOLLAR_2022_win),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))



 Inside_NY2_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=sum(DOLLAR_2022_win),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))

 Inside_NY3_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=sum(DOLLAR_2022_win),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))




 dropped_values_NY_1_2_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=sum(DOLLAR_2022_win),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))

 dropped_values_NY_2_3_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022_win=sum(DOLLAR_2022_win),OPERATING_PROFIT_2022_win=sum(OPERATING_PROFIT_2022_win))


```


# Average Scallop revenue and Operating Profit by NY 1, 2, and 3 and dropped values. GC fleet
```{r}

 Inside_NY1_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=mean(DOLLAR_2022),OPERATING_PROFIT_2022_win=mean(OPERATING_PROFIT_2022_win), LANDED_win=mean(LANDED_win),VPUE_win=mean(VPUE_win) )



 Inside_NY2_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=mean(DOLLAR_2022),OPERATING_PROFIT_2022_win=mean(OPERATING_PROFIT_2022_win), LANDED_win=mean(LANDED_win),VPUE_win=mean(VPUE_win) )

 Inside_NY3_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=mean(DOLLAR_2022),OPERATING_PROFIT_2022_win=mean(OPERATING_PROFIT_2022_win), LANDED_win=mean(LANDED_win),VPUE_win=mean(VPUE_win) )


 dropped_values_NY_1_2_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=mean(DOLLAR_2022),OPERATING_PROFIT_2022_win=mean(OPERATING_PROFIT_2022_win), LANDED_win=mean(LANDED_win),VPUE_win=mean(VPUE_win) )



 dropped_values_NY_2_3_GC %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(), DOLLAR_2022=mean(DOLLAR_2022),OPERATING_PROFIT_2022_win=mean(OPERATING_PROFIT_2022_win), LANDED_win=mean(LANDED_win),VPUE_win=mean(VPUE_win) )
```






# Average Revenue, Operating Profit, Landed, and VPUE in closures by fleet LA 

```{r}

 Inside_NY1_LA %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=mean(DOLLAR_2022),OPERATING_PROFIT_2022_win=mean(OPERATING_PROFIT_2022_win), LANDED_win=mean(LANDED_win),VPUE_win=mean(VPUE_win) )



 Inside_NY2_LA %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=mean(DOLLAR_2022),OPERATING_PROFIT_2022_win=mean(OPERATING_PROFIT_2022_win), LANDED_win=mean(LANDED_win),VPUE_win=mean(VPUE_win) )

 Inside_NY3_LA %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=mean(DOLLAR_2022),OPERATING_PROFIT_2022_win=mean(OPERATING_PROFIT_2022_win), LANDED_win=mean(LANDED_win),VPUE_win=mean(VPUE_win) )




 dropped_values_NY_1_2_LA %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=mean(DOLLAR_2022),OPERATING_PROFIT_2022_win=mean(OPERATING_PROFIT_2022_win), LANDED_win=mean(LANDED_win),VPUE_win=mean(VPUE_win) )



 dropped_values_NY_2_3_LA %>%
  group_by(fleet) %>%
  dplyr::summarise(Trips=n(),DOLLAR_2022=mean(DOLLAR_2022),OPERATING_PROFIT_2022_win=mean(OPERATING_PROFIT_2022_win), LANDED_win=mean(LANDED_win),VPUE_win=mean(VPUE_win) )





```



<br><br><br>

GC-IFQ Testing 
```{r}
## Phase 1

BSDA::z.test(dropped_values_NY_1_2_GC$DOLLAR_2022_win,
  y = Inside_NY2_GC$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_GC$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_GC$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_1_2_GC$DOLLAR_2022_win,
  y = Inside_NY2_GC$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_GC$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_GC$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_1_2_GC$DOLLAR_2022_win,
  y = Inside_NY2_GC$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_GC$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_GC$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2

BSDA::z.test(dropped_values_NY_2_3_GC$DOLLAR_2022_win,
  y = Inside_NY2_GC$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_GC$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_GC$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_2_3_GC$DOLLAR_2022_win,
  y = Inside_NY2_GC$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_GC$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_GC$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_2_3_GC$DOLLAR_2022_win,
  y = Inside_NY2_GC$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_GC$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_GC$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```


Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_NY_1_2_AA$DOLLAR_2022_win,
  y = Inside_NY2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_1_2_AA$DOLLAR_2022_win,
  y = Inside_NY2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_1_2_AA$DOLLAR_2022_win,
  y = Inside_NY2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_NY_2_3_AA$DOLLAR_2022_win,
  y = Inside_NY2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_2_3_AA$DOLLAR_2022_win,
  y = Inside_NY2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_2_3_AA$DOLLAR_2022_win,
  y = Inside_NY2_AA$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_AA$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_AA$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_NY_1_2_DAS$DOLLAR_2022_win,
  y = Inside_NY2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_1_2_DAS$DOLLAR_2022_win,
  y = Inside_NY2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_1_2_DAS$DOLLAR_2022_win,
  y = Inside_NY2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3

BSDA::z.test(dropped_values_NY_2_3_DAS$DOLLAR_2022_win,
  y = Inside_NY2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_2_3_DAS$DOLLAR_2022_win,
  y = Inside_NY2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_2_3_DAS$DOLLAR_2022_win,
  y = Inside_NY2_DAS$DOLLAR_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_DAS$DOLLAR_2022_win),
  sigma.y = sd(Inside_NY2_DAS$DOLLAR_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```




<br><br><br>
GC-IFQ z-tests
```{r}
## Phase 1
BSDA::z.test(dropped_values_NY_1_2_GC$LANDED_win,
  y = Inside_NY2_GC$LANDED_win,
  sigma.x = sd(dropped_values_NY_1_2_GC$LANDED_win),
  sigma.y = sd(Inside_NY2_GC$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_NY_1_2_GC$LANDED_win,
  y = Inside_NY2_GC$LANDED_win,
  sigma.x = sd(dropped_values_NY_1_2_GC$LANDED_win),
  sigma.y = sd(Inside_NY2_GC$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)

BSDA::z.test(dropped_values_NY_1_2_GC$LANDED_win,
  y = Inside_NY2_GC$LANDED_win,
  sigma.x = sd(dropped_values_NY_1_2_GC$LANDED_win),
  sigma.y = sd(Inside_NY2_GC$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2

BSDA::z.test(dropped_values_NY_2_3_GC$LANDED_win,
  y = Inside_NY2_GC$LANDED_win,
  sigma.x = sd(dropped_values_NY_2_3_GC$LANDED_win),
  sigma.y = sd(Inside_NY2_GC$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_NY_2_3_GC$LANDED_win,
  y = Inside_NY2_GC$LANDED_win,
  sigma.x = sd(dropped_values_NY_2_3_GC$LANDED_win),
  sigma.y = sd(Inside_NY2_GC$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)

BSDA::z.test(dropped_values_NY_2_3_GC$LANDED_win,
  y = Inside_NY2_GC$LANDED_win,
  sigma.x = sd(dropped_values_NY_2_3_GC$LANDED_win),
  sigma.y = sd(Inside_NY2_GC$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


```


<br><br><br>



Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_NY_1_2_AA$LANDED_win,
  y = Inside_NY2_AA$LANDED_win,
  sigma.x = sd(dropped_values_NY_1_2_AA$LANDED_win),
  sigma.y = sd(Inside_NY2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_1_2_AA$LANDED_win,
  y = Inside_NY2_AA$LANDED_win,
  sigma.x = sd(dropped_values_NY_1_2_AA$LANDED_win),
  sigma.y = sd(Inside_NY2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_1_2_AA$LANDED_win,
  y = Inside_NY2_AA$LANDED_win,
  sigma.x = sd(dropped_values_NY_1_2_AA$LANDED_win),
  sigma.y = sd(Inside_NY2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_NY_2_3_AA$LANDED_win,
  y = Inside_NY2_AA$LANDED_win,
  sigma.x = sd(dropped_values_NY_2_3_AA$LANDED_win),
  sigma.y = sd(Inside_NY2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_2_3_AA$LANDED_win,
  y = Inside_NY2_AA$LANDED_win,
  sigma.x = sd(dropped_values_NY_2_3_AA$LANDED_win),
  sigma.y = sd(Inside_NY2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_2_3_AA$LANDED_win,
  y = Inside_NY2_AA$LANDED_win,
  sigma.x = sd(dropped_values_NY_2_3_AA$LANDED_win),
  sigma.y = sd(Inside_NY2_AA$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_NY_1_2_DAS$LANDED_win,
  y = Inside_NY2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_NY_1_2_DAS$LANDED_win),
  sigma.y = sd(Inside_NY2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_1_2_DAS$LANDED_win,
  y = Inside_NY2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_NY_1_2_DAS$LANDED_win),
  sigma.y = sd(Inside_NY2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_1_2_DAS$LANDED_win,
  y = Inside_NY2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_NY_1_2_DAS$LANDED_win),
  sigma.y = sd(Inside_NY2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_NY_2_3_DAS$LANDED_win,
  y = Inside_NY2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_NY_2_3_DAS$LANDED_win),
  sigma.y = sd(Inside_NY2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_2_3_DAS$LANDED_win,
  y = Inside_NY2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_NY_2_3_DAS$LANDED_win),
  sigma.y = sd(Inside_NY2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_2_3_DAS$LANDED_win,
  y = Inside_NY2_DAS$LANDED_win,
  sigma.x = sd(dropped_values_NY_2_3_DAS$LANDED_win),
  sigma.y = sd(Inside_NY2_DAS$LANDED_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```






<br><br><br>

##GCIFQ Test 

```{r}
# Phase 1 to 2 
BSDA::z.test(dropped_values_NY_1_2_GC$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY2_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_NY_1_2_GC$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY2_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_1_2_GC$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY2_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Phase 2 to 3 

BSDA::z.test(dropped_values_NY_2_3_GC$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY3_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_NY_2_3_GC$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY3_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_2_3_GC$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_GC$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_GC$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY3_GC$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)
```


<br><br><br>

Limited Access z-tests
```{r}

# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_NY_1_2_AA$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_1_2_AA$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_1_2_AA$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY2_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_NY_2_3_AA$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY3_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_2_3_AA$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY3_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_2_3_AA$OPERATING_PROFIT_2022_win,
  y = Inside_NY3_AA$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_AA$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY3_AA$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_NY_1_2_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_1_2_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_1_2_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_1_2_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY2_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_NY_2_3_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY3_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_2_3_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY3_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_2_3_DAS$OPERATING_PROFIT_2022_win,
  y = Inside_NY2_DAS$OPERATING_PROFIT_2022_win,
  sigma.x = sd(dropped_values_NY_2_3_DAS$OPERATING_PROFIT_2022_win),
  sigma.y = sd(Inside_NY3_DAS$OPERATING_PROFIT_2022_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```




<br><br><br>

<br><br><br>

##GCIFQ Test 

```{r}
# Phase 1 to 2 
BSDA::z.test(dropped_values_NY_1_2_GC$VPUE_win,
  y = Inside_NY2_GC$VPUE_win,
  sigma.x = sd(dropped_values_NY_1_2_GC$VPUE_win),
  sigma.y = sd(Inside_NY2_GC$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_NY_1_2_GC$VPUE_win,
  y = Inside_NY2_GC$VPUE_win,
  sigma.x = sd(dropped_values_NY_1_2_GC$VPUE_win),
  sigma.y = sd(Inside_NY2_GC$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_1_2_GC$VPUE_win,
  y = Inside_NY2_GC$VPUE_win,
  sigma.x = sd(dropped_values_NY_1_2_GC$VPUE_win),
  sigma.y = sd(Inside_NY2_GC$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Phase 2 to 3 

BSDA::z.test(dropped_values_NY_2_3_GC$VPUE_win,
  y = Inside_NY2_GC$VPUE_win,
  sigma.x = sd(dropped_values_NY_2_3_GC$VPUE_win),
  sigma.y = sd(Inside_NY3_GC$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)

BSDA::z.test(dropped_values_NY_2_3_GC$VPUE_win,
  y = Inside_NY2_GC$VPUE_win,
  sigma.x = sd(dropped_values_NY_2_3_GC$VPUE_win),
  sigma.y = sd(Inside_NY3_GC$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_2_3_GC$VPUE_win,
  y = Inside_NY2_GC$VPUE_win,
  sigma.x = sd(dropped_values_NY_2_3_GC$VPUE_win),
  sigma.y = sd(Inside_NY3_GC$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)
```


<br><br><br>

Limited Access z-tests
```{r}
# LA 
## Phase 1 to 2

BSDA::z.test(dropped_values_NY_1_2_LA$VPUE_win,
  y = Inside_NY2_LA$VPUE_win,
  sigma.x = sd(dropped_values_NY_1_2_LA$VPUE_win),
  sigma.y = sd(Inside_NY2_LA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_1_2_LA$VPUE_win,
  y = Inside_NY2_LA$VPUE_win,
  sigma.x = sd(dropped_values_NY_1_2_LA$VPUE_win),
  sigma.y = sd(Inside_NY2_LA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_1_2_LA$VPUE_win,
  y = Inside_NY2_LA$VPUE_win,
  sigma.x = sd(dropped_values_NY_1_2_LA$VPUE_win),
  sigma.y = sd(Inside_NY2_LA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_NY_2_3_LA$VPUE_win,
  y = Inside_NY2_LA$VPUE_win,
  sigma.x = sd(dropped_values_NY_2_3_LA$VPUE_win),
  sigma.y = sd(Inside_NY3_LA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_2_3_LA$VPUE_win,
  y = Inside_NY2_LA$VPUE_win,
  sigma.x = sd(dropped_values_NY_2_3_LA$VPUE_win),
  sigma.y = sd(Inside_NY3_LA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_2_3_LA$VPUE_win,
  y = Inside_NY3_LA$VPUE_win,
  sigma.x = sd(dropped_values_NY_2_3_LA$VPUE_win),
  sigma.y = sd(Inside_NY3_LA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



# Access Area 
## Phase 1 to 2

BSDA::z.test(dropped_values_NY_1_2_AA$VPUE_win,
  y = Inside_NY2_AA$VPUE_win,
  sigma.x = sd(dropped_values_NY_1_2_AA$VPUE_win),
  sigma.y = sd(Inside_NY2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_1_2_AA$VPUE_win,
  y = Inside_NY2_AA$VPUE_win,
  sigma.x = sd(dropped_values_NY_1_2_AA$VPUE_win),
  sigma.y = sd(Inside_NY2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_1_2_AA$VPUE_win,
  y = Inside_NY2_AA$VPUE_win,
  sigma.x = sd(dropped_values_NY_1_2_AA$VPUE_win),
  sigma.y = sd(Inside_NY2_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)

## Phase 2 to 3
BSDA::z.test(dropped_values_NY_2_3_AA$VPUE_win,
  y = Inside_NY2_AA$VPUE_win,
  sigma.x = sd(dropped_values_NY_2_3_AA$VPUE_win),
  sigma.y = sd(Inside_NY3_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_2_3_AA$VPUE_win,
  y = Inside_NY2_AA$VPUE_win,
  sigma.x = sd(dropped_values_NY_2_3_AA$VPUE_win),
  sigma.y = sd(Inside_NY3_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_2_3_AA$VPUE_win,
  y = Inside_NY3_AA$VPUE_win,
  sigma.x = sd(dropped_values_NY_2_3_AA$VPUE_win),
  sigma.y = sd(Inside_NY3_AA$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


# Days-at-Sea
## Phase 1 to 2

BSDA::z.test(dropped_values_NY_1_2_DAS$VPUE_win,
  y = Inside_NY2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_NY_1_2_DAS$VPUE_win),
  sigma.y = sd(Inside_NY2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_1_2_DAS$VPUE_win,
  y = Inside_NY2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_NY_1_2_DAS$VPUE_win),
  sigma.y = sd(Inside_NY2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_1_2_DAS$VPUE_win,
  y = Inside_NY2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_NY_1_2_DAS$VPUE_win),
  sigma.y = sd(Inside_NY2_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)


## Phase 2 to 3
BSDA::z.test(dropped_values_NY_2_3_DAS$VPUE_win,
  y = Inside_NY2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_NY_2_3_DAS$VPUE_win),
  sigma.y = sd(Inside_NY3_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.90)


BSDA::z.test(dropped_values_NY_2_3_DAS$VPUE_win,
  y = Inside_NY2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_NY_2_3_DAS$VPUE_win),
  sigma.y = sd(Inside_NY3_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.95)


BSDA::z.test(dropped_values_NY_2_3_DAS$VPUE_win,
  y = Inside_NY2_DAS$VPUE_win,
  sigma.x = sd(dropped_values_NY_2_3_DAS$VPUE_win),
  sigma.y = sd(Inside_NY3_DAS$VPUE_win),
  alternative = c("two.sided"),
  conf.level = 0.99)



```


