---
title: "Scallop Data Summary"
author: "Alan Haynie, Melanie Harsch, Bryce McManus"
date: '`r Sys.Date()`'
output:
  html_document:
    keep_md: yes
    toc: true
    toc_float: true
    code_folding: show
params:
    AA_DAS_only: TRUE
    subtrip_aggregate: TRUE
    BIN_GEARS: TRUE
    location: 
      label: "Location:"
      value: Woods_Hole
      input: select
      choices: [Woods_Hole, Seattle]
    input_shapefile:
      value: "wind_sf_nocable.RDS"
      choices: ["wind_sf_final.RDS","wind_sf_nocable.RDS"]

---
<!---
YAML options: 


location --- NEFSC folks should set location=Woods_Hole. AK folks should set it to Seattle. This just controls where the data is read in from.

PreRelease -- controls the location of FishSET package. Set to FALSE to load without options. Set to TRUE to load from a particular lib.loc
--->
## Warning and Options
Please be careful with interpretation. Some outputs are uninterpretable when certain options are selected. For example, when we *do not* aggregate subtrips to trips:

1. the "per-unit-effort" outputs are not meaningful. 
2. Any statistics that are averaged are now averaged over subtrips, so this may not have a meaning either.

There may be other, so think carefully.

1.  Your location is  `r params$location`.
2.  The value of AA_DAS is `r params$AA_DAS_only`.
3.  The value of subtrip_aggregate is `r params$subtrip_aggregate`.
4.  The value of  BIN_GEARS is `r params$BIN_GEARS`.
5.  The input shapefile has been set to   `r params$input_shapefile`.



## Introduction 
 
This summary was done using a combination of FishSET console functions, the tidyverse
(mainly dplyr and tidyr), and a few formatting functions. There is an option to hide 
the code chunks at the top and a floating table of contents. All results are included in the 
output (apologies for the general messiness). You'll need to download the html
file to view the results (if you try to view the html file in Google Drive it will 
only show the raw html). 

This is a small Rmd that creates summary statistics for "all data" and for each fleet. Note, we winsorized our metrics at the fleet level.


<br><br>

## Library

```{r setup, echo=FALSE}
library(FishSET)

#library("tidyverse")
tidyverse_short <- c("dplyr",  "ggplot2", "magrittr", "tidyr", "lubridate") 
lapply(tidyverse_short, require, character.only = TRUE)
rm(tidyverse_short)
library(kableExtra) # table formatting 
library(sf) # converting geometry points to separate cols
library(here)
here::i_am("analysis_code/scallop_analysis_0322.Rmd")
# helper functions
source(here("analysis_code", "format_helpers.R"))

dir.create(here("data", "main","casestudies"), showWarnings="FALSE")


project <- "scallop0322"
pounds_to_kg<-2.20462
# disable scientific notation
options(scipen=999)

AA_DAS_param_hack <-params$AA_DAS_only
```




<br><br>

## Reset project

FishSET stores data in a directory called "FishSETFolder".  You can put this directory anywhere you want.

This chunk "resets" my project by erasing it. This is just to keep things tidy and
avoid potential errors when kitting the doc. 

At the dialog box, select the directory that contains the "FishSETFolder" or the directory in which you want the "FishSETFolder" to be created.  But don't select the "FishSETFolder" directory itself. 

If you don't have a FishSETFolder, the subsequent ``load_maindat()'' in the data_readin chunk will probably fail. The easiest thing to do is to create a FishSETFolder.  

```{r project_cleanup,eval=TRUE}

  folderpath <- here("FishSETFolder")
  proj_dir<-here()
  unlink(here(folderpath,project), recursive = TRUE)

```




<br><br>

## Data Import

```{r data_readin, eval=TRUE}
#For Woods_Hole users, read in the most recent data in data/main

if (params$location=="Woods_Hole"){
  # This code looks into /data/main and sets the vintage_string according to 
  # the most recent data
  datasets_list <- list.files(path = here("data", "main"), pattern = "final_product_lease")
  datasets_list <- gsub("final_product_lease_", "", datasets_list )
  datasets_list <- gsub("final_product_lease", "", datasets_list )
  datasets_list <- gsub(".Rds", "", datasets_list)
  datasets_list <- gsub(".csv" ,"", datasets_list)
  vintage_string <- max(datasets_list)
  rm(datasets_list)
  dat_filepath <- here("data", "main", paste0("final_product_lease_", vintage_string, ".Rds"))
} else if (params$location=="Seattle"){
  dat_filepath <- paste0("~/NE Scallops/data/updated/", 
                         "June 22/NE NW Collab/",
                         "final_product_lease_2022_05_25.Rds")
}

final_product_lease <- readRDS(dat_filepath)
# needed to rename this for now since it matches the name outputted from the
# zone assignment function we use. 
final_product_lease <- final_product_lease %>% rename(Zone_ID = "ZoneID") 
final_product_lease$scallop_fishing_year<-as.numeric(final_product_lease$scallop_fishing_year)

# convert the scallop_fishing_year variable into a "date" format that is amenable to the vessel_count() function
final_product_lease$scallop_fishing_yearD <- lubridate::date_decimal(final_product_lease$scallop_fishing_year)


final_product_lease <- final_product_lease %>%
  mutate(KILOGRAMS = POUNDS/pounds_to_kg,LANDED_KG=LANDED/pounds_to_kg) 


# converted column types to be compatible with tiny report  
final_product_lease$IMGID <- as.numeric(final_product_lease$IMGID)
final_product_lease$DEALER_RPT_ID <- as.numeric(final_product_lease$DEALER_RPT_ID)
final_product_lease$VTR_PORTNUM<- as.integer(final_product_lease$VTR_PORTNUM)
final_product_lease$YEAR<-as.integer(final_product_lease$YEAR)
final_product_lease$PERMIT.y<- as.integer(final_product_lease$PERMIT.y)
final_product_lease$DEALNUM<- as.integer(final_product_lease$DEALNUM)

#A column of ones. Useful for many things
final_product_lease$ones<-1



load_maindata(dat = final_product_lease, project = project, over_write = TRUE)

```
<br><br>

### Spatial data
Since sqlite can't save spatial data, we save it as a GeoJSON file in the project's 
data folder.
```{r}
 ten_filepath <- here("data", "external", "shapefiles", 
                      "Ten Minute Squares Cut North and Greater Atlantic")

# loads lease area combined w/ cable routes (saved locally) created from
# data_wrangle/combine_cable_routes.Rmd
lease_filepath <- here("data", "main", "spatial", params$input_shapefile)

load_spatial(lease_filepath, name = "WindClose", over_write = TRUE, project,
             data.type = "RDS")
load_spatial(ten_filepath, name = "TenMNSQR", over_write = TRUE, project,
             data.type = "shape")

scallop0322TenMNSQRSpatTable <- table_view("scallop0322TenMNSQRSpatTable", 
                                           project)
scallop0322WindCloseSpatTable <- table_view("scallop0322WindCloseSpatTable",
                                            project)
```

<br><br>

This data contains `r nrow(scallop0322MainDataTable)` rows and 
`r ncol(scallop0322MainDataTable)` variables. 

<br><br>

## Assign Fleets and Subset
We will want to do this before the rest of the QA/QC. There are always lots of broken bits, but many of them are going to be in the "other" fleet.

### Fleet assignment

```{r}
#Parse the first 2 digits of Area Identifier
scallop0322MainDataTable <-
  scallop0322MainDataTable %>% 
  mutate(`Area_ID2` = substr(`Area Identifier`, 1, 2))
```

```{r create_fleet_tabs}
 fleet_tab_AA_DAS <- data.frame(
  
  condition = c('`Plan Code` == "SES" & `Program Code` == "SAA"',
                '`Plan Code` == "SES" & `Program Code` == "SCA"',
                '`Plan Code` == "SES" & `Program Code` == "SCG" & `Area_ID2` != "NG"',
                '`Plan Code` == "SES" & `Program Code` == "SCG" & `Area_ID2` == "NG"'),
  fleet = c("Access Area", "Days at Sea", "GCIFQ", "GCNGOM")
)
  fleet_tab_LA_GC_IFQ <- data.frame(
  
  condition = c('`Plan Code` == "SES" & `Program Code` == "SAA" | 
                `Plan Code` == "SES" & `Program Code` == "SCA"',
                '`Plan Code` == "SES" & `Program Code` == "SCG" & `Area_ID2` != "NG"',
                '`Plan Code` == "SES" & `Program Code` == "SCG" & `Area_ID2` == "NG"'),
  fleet = c("Limited Access", "GCIFQ", "GCNGOM")
  )

```


```{r}
# save fleet appropriate table to FishSET DB


if (params$AA_DAS_only==TRUE){
 fleet_table(scallop0322MainDataTable, 
            project = project,
            table = fleet_tab_AA_DAS, save = TRUE)
} else if (params$AA_DAS_only==FALSE){
  fleet_table(scallop0322MainDataTable, 
            project = project,
            table = fleet_tab_LA_GC_IFQ, save = TRUE)
}
  

# Create fleet column 
fleet_tab_name <- list_tables(project, type = "fleet") # grab tab name

scallop0322MainDataTable <- 
  fleet_assign(scallop0322MainDataTable, project = project, 
               fleet_tab = fleet_tab_name)

# keep only rows corresponding to the 3 fleets that we care about.
scallop0322MainDataTable <-scallop0322MainDataTable %>%
  dplyr::filter(fleet %in%c("Access Area", "Days at Sea", "GCIFQ"))


```

<br><br>

### Bin Gears
```{r bin_gears}
if (params$BIN_GEARS==TRUE){

scallop0322MainDataTable$GEARCODE_OLD<-scallop0322MainDataTable$GEARCODE
#Anything with "DREDGE" in the GEARCODE will be rebinned to "DREDGE" 
pat_match<-"*DREDGE*"
reg_pat<-glob2rx(pat_match)
scallop0322MainDataTable$GEARCODE[grep(reg_pat,scallop0322MainDataTable$GEARCODE)]<-'DREDGE'
#Look at the GEARCODE NOW, there should be 'DREDGE', 'TRAWL-BOTTOM', and some funky stuff
table(scallop0322MainDataTable$GEARCODE)
scallop0322MainDataTable$GEARCODE[!(scallop0322MainDataTable$GEARCODE %in%c('DREDGE','TRAWL-BOTTOM'))]<-'OTHER'
}
```

## Aggregate subtrips to trips

The input data ``final_product_lease`` contains subtrips, not trips. This code chunk contracts trips to a single row, applying subtrip attributes for the most valuable subtrip (``max(DOLLAR)``)to the entire trip.

```{r construct_trip_aggregates, echo=TRUE, eval=TRUE}

if (params$subtrip_aggregate==TRUE){

# aggregate DOLLAR, POUNDS, LANDED by TRIPID and filter by max(DOLLAR)
scallop0322MainDataTable <- 
  scallop0322MainDataTable %>%
  group_by(TRIPID) %>%
  mutate(Agg_DOLLAR = sum(DOLLAR),Agg_DOLLAR_2022 = sum(DOLLAR_2022),  Agg_POUNDS = sum(POUNDS), Agg_LANDED = sum(LANDED), Agg_DOLLAR_ALL_SP_2022 = sum(DOLLAR_ALL_SP_2022))%>% 
  arrange(desc(DOLLAR)) %>%
  dplyr::filter(row_number()==1) %>% 
  dplyr::select(-DOLLAR, -POUNDS, -LANDED,-DOLLAR_ALL_SP_2022, -DOLLAR_2022) %>% 
  rename(DOLLAR = "Agg_DOLLAR", POUNDS = "Agg_POUNDS", LANDED = "Agg_LANDED", DOLLAR_ALL_SP_2022 = "Agg_DOLLAR_ALL_SP_2022", DOLLAR_2022="Agg_DOLLAR_2022") %>% 
  ungroup()

scallop0322MainDataTable <- scallop0322MainDataTable %>%
  mutate(KILOGRAMS = POUNDS/pounds_to_kg,
         LANDED_KG=LANDED/pounds_to_kg)



## Test out 
sum(duplicated(scallop0322MainDataTable$TRIPID))
stopifnot(sum(duplicated(scallop0322MainDataTable$TRIPID))==0)
}
```


```{r calculate operating profit, echo=TRUE, eval=TRUE}

#Calculate operating profit by subtracting nominal trip costs from nominal aggregated revenues. Then deal with real. 
scallop0322MainDataTable$OPERATING_PROFIT <- 
  (scallop0322MainDataTable$DOLLAR_ALL_SP - scallop0322MainDataTable$TRIP_COST_NOMINALDOLS_WINSOR)


scallop0322MainDataTable$OPERATING_PROFIT_2022 <- 
  (scallop0322MainDataTable$DOLLAR_ALL_SP_2022 - scallop0322MainDataTable$TRIP_COST_WINSOR_2022_DOL)


```


<br><br>

### Duplicate trip IDs

```{r}
# add a duplicate trip column
dup_ind <- duplicated(scallop0322MainDataTable$TRIPID)
dup_ids <- unique(scallop0322MainDataTable$TRIPID[dup_ind])

scallop0322MainDataTable <- 
  scallop0322MainDataTable %>% 
  mutate(dup_trip = TRIPID %in% dup_ids)

# number of obs from duplicate tripIDs 
sum(scallop0322MainDataTable$dup_trip)
```


<br><br>

## QAQC

This section includes our standard QAQC checks. Here I'm only checking whether 
a potential issue exists and not changing the data in any way (except in the
empty variable section).

<br><br>

### NA check
```{r}
na_filter(scallop0322MainDataTable, 
          project = project, 
          replace = FALSE, remove = FALSE, 
          rep.value = NA, over_write = FALSE)
```

<br><br>

### NaN check
```{r}
nan_filter(scallop0322MainDataTable, 
           project = project, 
           replace = FALSE, remove = FALSE, 
           rep.value = NA, over_write = FALSE)
```

<br><br>

### Unique rows

```{r}
unique_filter(scallop0322MainDataTable, project = project, remove = FALSE)
```
<br><br>

### Empty variables
By "empty" we mean containing all NAs.
```{r}
empty_vars_filter(scallop0322MainDataTable, project = project, remove = FALSE)

```

<br><br>


### Lon/Lat format

```{r, eval=FALSE}
degree(scallop0322MainDataTable, project = project,
       lat = "DDLAT", lon = "DDLON", 
       latsign = NULL, lonsign = NULL,
       replace = FALSE)
```
<br><br>

### Spatial QAQC 

```{r, eval=FALSE}
spat_qaqc_out <-
spatial_qaqc(scallop0322MainDataTable, project = project,
             spat = scallop0322TenMNSQRSpatTable, lon.dat = "DDLON", lat.dat = "DDLAT")

spat_qaqc_out$dataset <- NULL # drop dataset
spat_qaqc_out$spatial_summary %>% 
  pretty_lab(cols = "n") %>% 
   pretty_tab() 
spat_qaqc_out[2:4]
```
<br><br>

## Data creation

### Finagle Live pounds to meat weights
```{r}
# rename POUNDS to LIVE_POUNDS for clarity.  Convert live pounds to meat pounds.
scallop0322MainDataTable$LIVE_POUNDS <- scallop0322MainDataTable$POUNDS
scallop0322MainDataTable$MEAT_POUNDS <- scallop0322MainDataTable$POUNDS/8.33
scallop0322MainDataTable$POUNDS <-NULL

scallop0322MainDataTable$LIVE_KG <- scallop0322MainDataTable$LIVE_POUNDS/pounds_to_kg
scallop0322MainDataTable$MEAT_KG <- scallop0322MainDataTable$MEAT_POUNDS/pounds_to_kg



```





### CPUE
Here I creating a CPUE variable using TRIP_LENGTH and MEAT_KG. I'm also filtering
out any infinite values. 
```{r}
scallop0322MainDataTable <- 
  cpue(scallop0322MainDataTable, project,
       xWeight = "MEAT_KG",
       xTime = "TRIP_LENGTH", 
       name = "CPUE")

scallop0322MainDataTable <- 
  scallop0322MainDataTable %>% 
  filter(!is.infinite(CPUE))
```
<br><br>

### VPUE
Same as above but with revenue instead of meat KG 
```{r}
scallop0322MainDataTable <- 
  cpue(scallop0322MainDataTable, project,
       xWeight = "DOLLAR_2022",
       xTime = "TRIP_LENGTH", 
       name = "VPUE")

scallop0322MainDataTable <- 
  scallop0322MainDataTable %>% 
  filter(!is.infinite(VPUE))
```
<br><br>


### Subset


```{r subset_fleet, eval=TRUE}

AA_data <- 
    scallop0322MainDataTable %>% 
    filter(fleet == "Access Area")


DAS_data <- 
    scallop0322MainDataTable %>% 
    filter(fleet == "Days at Sea")

GCIFQ_data <-
    scallop0322MainDataTable %>% 
    filter(fleet == "GCIFQ")

```




```{r Winsorize and stitch back together, eval=TRUE}

## AA fleet
AA_data <- AA_data %>%
dplyr::mutate(DOLLAR_2022_win=datawizard::winsorize(DOLLAR_2022, threshold = 0.01),
              LANDED_win = datawizard::winsorize(LANDED, threshold = 0.01),
           DOLLAR_ALL_SP_win = datawizard::winsorize(DOLLAR_ALL_SP_2022, threshold = 0.01),    
            VPUE_win = datawizard::winsorize(VPUE, threshold = 0.01)
)

AA_data <- AA_data %>%
  dplyr::mutate(OPERATING_PROFIT_2022_win=DOLLAR_ALL_SP_win - TRIP_COST_WINSOR_2022_DOL)

sum(is.na(AA_data$OPERATING_PROFIT_2022_win))
AA_data$OPERATING_PROFIT_2022_win[is.na(AA_data$OPERATING_PROFIT_2022_win)] <- mean(AA_data$OPERATING_PROFIT_2022_win, na.rm = TRUE)

## DAS fleet

DAS_data <- DAS_data %>%
dplyr::mutate(DOLLAR_2022_win=datawizard::winsorize(DOLLAR_2022, threshold = 0.01),
              LANDED_win = datawizard::winsorize(LANDED, threshold = 0.01),
           DOLLAR_ALL_SP_win = datawizard::winsorize(DOLLAR_ALL_SP_2022, threshold = 0.01),    
            VPUE_win = datawizard::winsorize(VPUE, threshold = 0.01)
)

DAS_data <- DAS_data %>%
  dplyr::mutate(OPERATING_PROFIT_2022_win=DOLLAR_ALL_SP_win - TRIP_COST_WINSOR_2022_DOL)

sum(is.na(DAS_data$OPERATING_PROFIT_2022_win))
DAS_data$OPERATING_PROFIT_2022_win[is.na(DAS_data$OPERATING_PROFIT_2022_win)] <- mean(DAS_data$OPERATING_PROFIT_2022_win, na.rm = TRUE)



## GCIFQ fleet

GCIFQ_data <-GCIFQ_data %>%
dplyr::mutate(DOLLAR_2022_win=datawizard::winsorize(DOLLAR_2022, threshold = 0.01),
              LANDED_win = datawizard::winsorize(LANDED, threshold = 0.01),
           DOLLAR_ALL_SP_win = datawizard::winsorize(DOLLAR_ALL_SP_2022, threshold = 0.01),    
            VPUE_win = datawizard::winsorize(VPUE, threshold = 0.01)
)


GCIFQ_data <- GCIFQ_data %>%
  dplyr::mutate(OPERATING_PROFIT_2022_win=DOLLAR_ALL_SP_win - TRIP_COST_WINSOR_2022_DOL)

sum(is.na(GCIFQ_data$OPERATING_PROFIT_2022_win))
GCIFQ_data$OPERATING_PROFIT_2022_win[is.na(GCIFQ_data$OPERATING_PROFIT_2022_win)] <- mean(GCIFQ_data$OPERATING_PROFIT_2022_win, na.rm = TRUE)

scallop0322MainDataTable<-rbind(AA_data, DAS_data)
scallop0322MainDataTable<-rbind(scallop0322MainDataTable, GCIFQ_data)


```


# Summary Statistics

### summary table
```{r}
summary_stats(scallop0322MainDataTable, project) %>% 
  pretty_tab_sb()
```


Here is DOLLAR, DOLLAR_ALL_SP_2022, LANDED, and TRIP_LENGTH separately. Probably need to add a count (N) and check fleets
```{r}
scallop0322MainDataTable %>% 
  summarize(across(.cols = c("DOLLAR_2022_win", "DOLLAR_ALL_SP_win","LANDED_win", "VPUE_win","OPERATING_PROFIT_2022_win"), 
                   .fns = list(min = min, median = median, mean = mean, sd=sd, max = max,
                               sum=sum, NAs = ~sum(is.na(.x)), UniqueObs = n_distinct, 
                               "No. 0's" = ~sum(.x == 0)), 
                   .names = "{.col}__{.fn}")) %>% 
  pivot_longer(cols = everything(), values_to = "value", names_to = "summary") %>% 
  pretty_lab() %>% 
  separate(col = "summary", sep = "__", into = c("var", "summary")) %>% 
  pivot_wider(names_from = "var", values_from = "value") %>% 
  pretty_tab()
 
```

Access Area Fleet summary statistics
```{r}
AA_data %>% 
  summarize(across(.cols = c("DOLLAR_2022_win", "DOLLAR_ALL_SP_win","LANDED_win", "VPUE_win","OPERATING_PROFIT_2022_win"), 
                   .fns = list(min = min, median = median, mean = mean, sd=sd, max = max,
                               sum=sum, NAs = ~sum(is.na(.x)), UniqueObs = n_distinct, 
                               "No. 0's" = ~sum(.x == 0)), 
                   .names = "{.col}__{.fn}")) %>% 
  pivot_longer(cols = everything(), values_to = "value", names_to = "summary") %>% 
  pretty_lab() %>% 
  separate(col = "summary", sep = "__", into = c("var", "summary")) %>% 
  pivot_wider(names_from = "var", values_from = "value") %>% 
  pretty_tab()
 
```
Days-at-Sea  Fleet summary statistics
```{r}

DAS_data %>% 
  summarize(across(.cols = c("DOLLAR_2022_win", "DOLLAR_ALL_SP_win","LANDED_win", "VPUE_win","OPERATING_PROFIT_2022_win"), 
                   .fns = list(min = min, median = median, mean = mean, sd=sd, max = max,
                               sum=sum, NAs = ~sum(is.na(.x)), UniqueObs = n_distinct, 
                               "No. 0's" = ~sum(.x == 0)), 
                   .names = "{.col}__{.fn}")) %>% 
  pivot_longer(cols = everything(), values_to = "value", names_to = "summary") %>% 
  pretty_lab() %>% 
  separate(col = "summary", sep = "__", into = c("var", "summary")) %>% 
  pivot_wider(names_from = "var", values_from = "value") %>% 
  pretty_tab()
```  
  
GCIFQ summary statistics  
```{r}
GCIFQ_data %>% 
  summarize(across(.cols = c("DOLLAR_2022_win", "DOLLAR_ALL_SP_win","LANDED_win", "VPUE_win","OPERATING_PROFIT_2022_win"), 
                   .fns = list(min = min, median = median, mean = mean, sd=sd, max = max,
                               sum=sum, NAs = ~sum(is.na(.x)), UniqueObs = n_distinct, 
                               "No. 0's" = ~sum(.x == 0)), 
                   .names = "{.col}__{.fn}")) %>% 
  pivot_longer(cols = everything(), values_to = "value", names_to = "summary") %>% 
  pretty_lab() %>% 
  separate(col = "summary", sep = "__", into = c("var", "summary")) %>% 
  pivot_wider(names_from = "var", values_from = "value") %>% 
  pretty_tab()
```


