---
title: "cross-check data"
output:
  pdf_document: default
  word_document: default
---
# Purpose
This is code to make sure that Greg, Min-Yang, and Marina's data processing produces the same data.  It reads in the "most recent" data from Greg, Min-Yang, and Marina's directories. It does a few basic checks, like listing the names of columns and rows of data. It also uses the all.equal() function to check if objects are the same. identical() could be used instead; no thought was put into this decision.

Although this written as a markdown doc, it is probably better to source the chunks, either all at a time, or in sequence, so the dataframes remain in R environment and you can examine them.


# Project setup
here(), load libraries, and set a data vintage. 

```{r setup, include=TRUE, echo=TRUE, results=FALSE}

# Set Path
here::i_am("data_wrangle/verify_identical_data.Rmd")

# Please ensure you have the proper packages installed with (install.packages()) or a request to ITD if any libraries do not load.  


library("here")
library("tidyverse")
library("dbplyr")
library("data.table")
library("arsenal")
vintage_string<-Sys.Date()
vintage_string<-gsub("-","_",vintage_string)

# Set path by hand. This a little sketchy code, but fine for this purpose. Probably don't reuse this
net<-network_location_desktop
net<-network_location_remote

lee_directory<-file.path(net,"home2", "mlee","Effort-Displacement---Scallop")
chaji_directory<-file.path(net,"home4", "mchaji","Effort-Displacement---Scallop")

ardini_directory<-file.path(net,"home1", "gardini","Effort-Displacement---Scallop")



```

```{r lookup_minyang_data,  eval=TRUE,include=TRUE}
#This code looks into min-yang's and sets the vintage_string according to the most recent data
datasets_list<-list.files(path=file.path(lee_directory,"data","main"), pattern="final_product_lease_")
datasets_list<-gsub("final_product_lease_","",datasets_list )
datasets_list<-gsub(".Rds","",datasets_list)
datasets_list<-gsub(".csv","",datasets_list)
lee_vintage_string<-max(datasets_list)
rm(datasets_list)
```
```{r readin_minyang_final_product,  eval=TRUE,include=TRUE}

final_product_lease_lee <- readRDS(file.path(lee_directory,"data","main",paste0("final_product_lease_",lee_vintage_string,".Rds")))
Scallop_Linkingorg_lee <- readRDS(file.path(lee_directory,"data","intermediate",paste0("Scallop_Linkingorg_",lee_vintage_string,".Rds")))
RESULT_COMPILED_lee <- readRDS(file.path(lee_directory,"data","intermediate",paste0("RESULT_COMPILED_",lee_vintage_string,".Rds")))


```




```{r lookup_marina_data,  eval=TRUE,include=TRUE}
#This code looks into min-yang's and sets the vintage_string according to the most recent data
datasets_list<-list.files(path=file.path(chaji_directory,"data","main"), pattern="final_product_lease_")
datasets_list<-gsub("final_product_lease_","",datasets_list )
datasets_list<-gsub(".Rds","",datasets_list)
datasets_list<-gsub(".csv","",datasets_list)
chaji_vintage_string<-max(datasets_list)
rm(datasets_list)
```

```{r readin_chaji_data, eval=TRUE,include=TRUE}
final_product_lease_chaji <- readRDS(file.path(chaji_directory,"data","main",paste0("final_product_lease_",chaji_vintage_string,".Rds")))

Scallop_Linkingorg_chaji <- readRDS(file.path(chaji_directory,"data","intermediate",paste0("Scallop_Linkingorg_",chaji_vintage_string,".Rds")))
RESULT_COMPILED_chaji <- readRDS(file.path(chaji_directory,"data","intermediate",paste0("RESULT_COMPILED_",chaji_vintage_string,".Rds")))


```



```{r lookup_greg_data, eval=TRUE,include=TRUE}
#This code looks into min-yang's and sets the vintage_string according to the most recent data
datasets_list<-list.files(path=file.path(ardini_directory,"data","main"), pattern="final_product_lease")
datasets_list<-gsub("final_product_lease","",datasets_list )
datasets_list<-gsub(".Rds","",datasets_list)
datasets_list<-gsub(".csv","",datasets_list)
ardini_vintage_string<-max(datasets_list)
rm(datasets_list)
```

```{r readin_ardini_data, eval=TRUE, include=TRUE}
final_product_lease_ardini <- readRDS(file.path(ardini_directory,"data","main",paste0("final_product_lease",ardini_vintage_string,".Rds")))
#Scallop_Linkingorg_ardini <- readRDS(file.path(ardini_directory,"data","intermediate",paste0("Scallop_Linkingorg_",ardini_vintage_string,".Rds")))
#RESULT_COMPILED_ardini <- readRDS(file.path(ardini_directory,"data","intermediate",paste0("RESULT_COMPILED_",ardini_vintage_string,".Rds")))

```

```{r check RESULT_COMPILED, eval=TRUE, include=TRUE, echo=TRUE, results=TRUE}
nrow(RESULT_COMPILED_chaji)
nrow(RESULT_COMPILED_lee)

# nrow(RESULT_COMPILED_ardini)

colnames(RESULT_COMPILED_chaji)
colnames(RESULT_COMPILED_lee)
# colnames(RESULT_COMPILED_ardini)

all.equal(RESULT_COMPILED_chaji, RESULT_COMPILED_lee)
#identical(RESULT_COMPILED_chaji, RESULT_COMPILED_lee)

# all.equal(RESULT_COMPILED_chaji, RESULT_COMPILED_ardini)

```


```{r check Scallop_Linkingorg, eval=TRUE, include=TRUE, echo=TRUE, results=TRUE}
nrow(Scallop_Linkingorg_chaji)
nrow(Scallop_Linkingorg_lee)

colnames(Scallop_Linkingorg_chaji)
colnames(Scallop_Linkingorg_lee)

all.equal(Scallop_Linkingorg_chaji, Scallop_Linkingorg_lee)
#identical(Scallop_Linkingorg_chaji, Scallop_Linkingorg_lee)

```


```{r check final_product_lease, eval=TRUE, include=TRUE, echo=TRUE, results=TRUE}
nrow(final_product_lease_chaji)
nrow(final_product_lease_lee)
nrow(final_product_lease_ardini)

colnames(final_product_lease_chaji)
colnames(final_product_lease_lee)
colnames(final_product_lease_ardini)


#all.equal(final_product_lease_chaji, final_product_lease_lee)
#identical(final_product_lease_chaji, final_product_lease_lee)

# Run this chunk if identical() or all.equal() results return as false
# comparedf(final_product_lease_chaji, final_product_lease_lee)
# summary(comparedf(final_product_lease_chaji, final_product_lease_lee))

```
